---
title: "Climate Crisis Iteration 1 Measurement Model Evaluation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(seminr)
library(data.table)
library(DT)
library(htmltools)
model <- readRDS("model-cc-1.RDS")
bootmodel <- readRDS("model-boot-cc-1.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumfsbo <- summary(bootmodel$first_stage_model)
```

# Model plots
## Original Estimate Path Model
This is the original estimate path model.
```{r plot model, echo=FALSE}
plot(model, title = "Original Estimate Model", theme = seminr_theme_smart())
```

## Bootstrapped Path Model
This is the bootstrapped path model.
```{r plot bootmodel, echo=FALSE}
plot(bootmodel, title = "Bootstrapped Model")
```

## Measurement Model Only
This is a path model showing only the measurement model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel, measurement_only = TRUE)
```
```{r eval-df, echo = FALSE, include=FALSE}
# Base DF
evalmm <- data.frame(Construct = model$mmMatrix[,1],
                           Type = ifelse(grepl("HOCA", model$mmMatrix[,3]),
                                         "HOC", "Construct"),
                           Mode = dplyr::recode(model$mmMatrix[,3],
                                         "A" = "reflective",
                                         "B" = "formative",
                                         "HOCA" = "higher-order"),
                           Indicator.or.LOC = model$mmMatrix[,2])

# hocevalmm1 <- evalmm %>% filter(Mode == "higher-order")%>% rename(LOC = Indicator.or.LOC) %>% mutate(Type = NULL)
# unique(hocevalmmcc1$Construct)
# forevalmmcc1 <- evalmmcc1 %>% filter(Mode == "formative") %>% rename(Indicator = Indicator.or.LOC) %>% mutate(Type = NULL)
# forevalmmcc1

```

# Evaluation of the reflective measurement model
```{r ref-eval prep, echo = FALSE, include=FALSE}
refevalmmbase <- evalmm %>% filter(Mode == "reflective") %>% rename(Indicator = Indicator.or.LOC) %>% 
  mutate(Type = NULL, Mode = NULL)
refloadings <- c()
for (i in 1:nrow(refevalmmbase)){
  refloadings <<- append(refloadings, sumfs$loadings[refevalmmbase$Indicator[i], refevalmmbase$Construct[i]])
}

cicr <- data.frame(Construct = row.names(sumfs$reliability), 
                   AVE = as.numeric(sumfs$reliability[,3]), 
                   Calpha = as.numeric(sumfs$reliability[,1]),
                   rhoC = as.numeric(sumfs$reliability[,2]))
#Next step is HTMT
boothtmtbase <- data.frame(Construct.Rel. = row.names(sumbomo$bootstrapped_HTMT),
                          Lower.CI = as.numeric(sumbomo$bootstrapped_HTMT[,5]),
                          Upper.CI = as.numeric(sumbomo$bootstrapped_HTMT[,6]))
#For HTMT evaluation, one should consider only reflective constructs - and HOCs with reflective LOCs
htmtvec <- c(unique(refevalmmbase$Construct), 
             unlist(unique(evalmm %>% filter(Indicator.or.LOC %in% unique(refevalmmbase$Construct)) %>% select("Construct"))))
# Transform "Relationships" Column into two distinct columns
boothtmtsplit <- base::strsplit(boothtmtbase$Construct.Rel., "  ->  ")
boothtmtsplit1 <- c()
boothtmtsplit2 <- c()
for (i in 1:length(boothtmtsplit)){
 boothtmtsplit1 <<- append(boothtmtsplit1, boothtmtsplit[[i]][1])
 boothtmtsplit2 <<- append(boothtmtsplit2, boothtmtsplit[[i]][2])
}
boothtmt <- (boothtmtbase %>% mutate(Construct.Rel. = NULL, Construct.1 = boothtmtsplit1, Construct.2 = boothtmtsplit2))[,c(3:4,1:2)] %>%
  filter(Construct.1 %in% htmtvec & Construct.2 %in% htmtvec)
maxhtmtbase <- data.frame(Construct = boothtmt[,1], Max.HTMT =  boothtmt[,4]) %>% 
  rbind(data.frame(Construct = boothtmt[,2], Max.HTMT =  boothtmt[,4])) %>%
  group_by(Construct) %>%
  summarise(Max.HTMT = max(Max.HTMT)) %>%
  mutate('1.in.HTMT.CI' = ifelse(Max.HTMT >=1, TRUE, FALSE))
`%notin%` <- Negate(`%in%`)
maxhtmt <- evalmm[,c(1,4)] %>% filter(Indicator.or.LOC %in% unique(refevalmmbase$Construct)) %>%
  rbind(data.frame(Construct = unique(refevalmmbase$Construct[refevalmmbase$Construct %notin% evalmm$Indicator.or.LOC]),
                   Indicator.or.LOC = unique(refevalmmbase$Construct[refevalmmbase$Construct %notin% evalmm$Indicator.or.LOC]))) %>%
  left_join(maxhtmtbase, ) %>% 
  mutate(Construct = Indicator.or.LOC, Indicator.or.LOC = NULL)

# Make final data frame
refevalmm <- refevalmmbase %>% cbind(Loadings = refloadings) %>% left_join(cicr) %>% left_join(maxhtmt[,c(1,3)])
```
```{r ref-eval, echo=FALSE}
datatable(refevalmm) %>%
  formatRound(3:6,
              digits = 3)
```

## Convergent validity
Ideally, outer loadings (<font face="Symbol">l</font>) should be $\geq$ 0.70. Loadings below 0.40 are unacceptable. AVE should be > 0.50. 

## Internal consistency reliability
Both Cronbach's <font face="Symbol">a</font> and composite reliability <font face="Symbol">r</font><sub>c</sub> should be $\geq$ 0.60 and $\leq$ 0.90. The upper threshold of acceptability is 0.95.

## Discriminant validity
Discriminant validity is evaluated using the hetereotrait-monotrait ratio (HTMT). The HTMT bootstrap confidence interval should not contain 1.

```{r ref-eval-HTMT,echo=FALSE}
#If there are problems with the HTMT, here is a detailed table
datatable(boothtmt) %>%
  formatRound(3:4,
              digits = 3)
```

# Evaluation of the formative measurement model
```{r for-eval prep, echo = FALSE, include=FALSE}
forevalbase <- evalmm %>% filter(Mode == "formative") %>% rename(Indicator = Indicator.or.LOC) %>% 
  mutate(Type = NULL, Mode = NULL)
```
## Convergent validity
To evaluate convergent validity, a redundancy analysis is conducted. The path coefficient should be $\geq$ 0.70 and R² should be $\geq$ 0.50.

### Perceived Self-Efficacy
```{r for-eval rapse, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
rapse <- readRDS("rapse-cc-1.RDS")
plot(rapse, title = "Redundancy Analysis Perceived Self-Efficacy", theme = seminr_theme_create(plot.adj = FALSE))
sumrapse <- summary(rapse)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvpse <- data.frame(Construct = "Perceived Self-Efficacy", 'C.V.R^2' = sumrapse$paths[1], 'C.V.PC' = sumrapse$paths[3])
```

### Perceived Response Efficacy
```{r for-eval rapre, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
rapre <- readRDS("rapre-cc-1.RDS")
plot(rapre, title = "Redundancy Analysis Perceived Response Efficacy", theme = seminr_theme_create(plot.adj = FALSE))
sumrapre <- summary(rapre)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvpre <- data.frame(Construct = "Perceived Response Efficacy", 'C.V.R^2' = sumrapre$paths[1], 'C.V.PC' = sumrapre$paths[3])
```

```{r for-eval raprc, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
raprc <- readRDS("raprc-cc-1.RDS")
plot(raprc, title = "Redundancy Analysis Perceived Response Costs", theme = seminr_theme_create(plot.adj = FALSE))
sumraprc <- summary(raprc)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvprc <- data.frame(Construct = "Perceived Response Costs", 'C.V.R^2' = sumraprc$paths[1], 'C.V.PC' = sumraprc$paths[3])
```

```{r for-eval radn, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
radn <- readRDS("radn-cc-1.RDS")
plot(radn, title = "Redundancy Analysis Descriptive Norm", theme = seminr_theme_create(plot.adj = FALSE))
sumradn <- summary(radn)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvdn <- data.frame(Construct = "Descriptive Norm", 'C.V.R^2' = sumradn$paths[1], 'C.V.PC' = sumradn$paths[3])
```

```{r for-eval rain, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
rain <- readRDS("rain-cc-1.RDS")
plot(rain, title = "Redundancy Analysis Injunctive Norm", theme = seminr_theme_create(plot.adj = FALSE))
sumrain <- summary(rain)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvin <- data.frame(Construct = "Injunctive Norm", 'C.V.R^2' = sumrain$paths[1], 'C.V.PC' = sumrain$paths[3])
```

```{r for-eval rabi, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
rabi <- readRDS("rabi-cc-1.RDS")
plot(rabi, title = "Redundancy Analysis Behavioral Intention", theme = seminr_theme_create(plot.adj = FALSE))
sumrabi <- summary(rabi)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvbi <- data.frame(Construct = "Behavioral Intention", 'C.V.R^2' = sumrabi$paths[1], 'C.V.PC' = sumrabi$paths[3])
```
```{r for-eval cv,echo=FALSE, include=FALSE}
# put together all dataframes, this has also to be done manually
forevalci <- bind_rows(cvpse, cvpre, cvprc, cvdn, cvin, cvbi)

```



```{r for-eval, echo=FALSE}
datatable(forevalmm) %>%
  formatRound(3:6,
              digits = 3)
```
