---
title: "Climate Crisis Model Iteration 2-c-2 (Driving) Structural Model Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
# Load models and create summaries
model <- readRDS("Models/model-cc-2-c-2.RDS")
bootmodel <- readRDS("Models/model-boot-cc-2-c-2.RDS")
bootfsmodel <- readRDS("Models/model-fs-boot-cc-2-c-2.RDS")
proxymodel <- readRDS("Models/model-proxy-cc-2-c-2.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Set seminr plot theme
thm <- seminr_theme_create(construct.compositeA.arrow = "backward", construct.compositeA.use_weights = FALSE, plot.adj = FALSE)
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots
## Structural Model Only
This is a path model showing only the structural model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel, structure_only = TRUE)
```

# Collinearity
Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.
```{r collinearity vif, echo = FALSE}
vif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(summo$vif_antecedents)){
  x = names(summo$vif_antecedents[i])
  for (j in 1:length(summo$vif_antecedents[[{{x}}]])){
    y = names(summo$vif_antecedents[[{{x}}]])[j]
    vif <- vif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = summo$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(sumfs$vif_antecedents)){
  x = names(sumfs$vif_antecedents[i])
  for (j in 1:length(sumfs$vif_antecedents[[{{x}}]])){
    y = names(sumfs$vif_antecedents[[{{x}}]])[j]
    locvif <- locvif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = sumfs$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- locvif %>% filter(!(Exogenous.Construct %in% vif$Exogenous.Construct & Endogenous.Construct %in% vif$Endogenous.Construct))
vif <- union(vif, locvif)
datatable(vif,
          filter = 'top',
          options = list(pageLength = nrow(vif)),
          rownames = FALSE,
          colnames = c('Exogenous Construct' = 1,
                        'Endogenous Construct' = 2),
          caption = 'Results of the structural collinearity assessment') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```
There is no collinearity as indicated by VIF. Some VIF values are above 3, but still below the critical value of 5. This is mainly the case for lower-order construct relationships.

# In-sample predictive power
In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.
```{r in-sample pp r^2, echo=FALSE}
r2hoc <- data.frame(Construct = colnames(summo$paths),
                    "R^2" = summo$paths[1,],
                    "AdjR^2" = summo$paths[2,])
r2loc <- data.frame(Construct = colnames(sumfs$paths),
                    "R^2" = sumfs$paths[1,],
                    "AdjR^2" = sumfs$paths[2,]) %>%
  filter(Construct %notin% r2hoc$Construct)
r2 <- union(r2hoc, r2loc)
datatable(r2,
          filter = 'top',
          options = list(pageLength = nrow(r2)),
          rownames = FALSE,
          colnames = c('R²' = 2,
                        'R²adj' = 3),
          caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.25,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```
R² for the lower-order constructs Perceived Response Costs and Perceived Self-Efficacy is below the critical threshold of 0.1.
Other than that, the lower-order construct Perceived Response Efficacy and the higher-order construct Response Beliefs are between 0.1 and 0.25, indicating very weak in-sample predictive power.
In-sample predictive power for all other constructs except Behavioral Intention is weak, as all R² values remain below 0.5.
The in-sample predictive power for Behavioral Intention is moderate.

# Effect size
Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
smhoc <- data.frame(model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target)
hocf2vec <- c()
for (i in 1:nrow(smhoc)){
  x = smhoc[i,1]
  y = smhoc[i, 2]
hocf2vec <- append(hocf2vec, summo$fSquare[[{{x}},{{y}}]])  
}
hocf2 <- smhoc %>% cbind(hocf2vec) %>% rename('f^2' = 3)
smloc <- data.frame(model$first_stage_model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target) %>%
  filter('Exogenous Construct' %notin% smhoc$`Exogenous Construct`)
locf2vec <- c()
for (i in 1:nrow(smloc)){
  x = smloc[i,1]
  y = smloc[i, 2]
locf2vec <- append(locf2vec, sumfs$fSquare[[{{x}},{{y}}]])  
}
locf2 <- smloc %>% cbind(locf2vec) %>% rename('f^2' = 3) %>% 
  filter(!(`Exogenous Construct` %in% hocf2$`Exogenous Construct` & `Endogenous Construct` %in% hocf2$`Endogenous Construct`))
f2 <- union(hocf2, locf2)
datatable(f2,
          filter = 'top',
          options = list(pageLength = nrow(f2)),
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.02), values = c('#ff9999', '#00')))
```
f² indicates negligible effect sizes for many of the relationships involving lower-order constructs.
In particular, there is no discernible effect of Integrity on any other lower-order construct.
Benevolence and Competence have only a discernible effect on Perceived Severity.
Additionally, there seems to be no discernible effect of Threat Beliefs on Behavioral Intention.
If this is mirrored in non-significant path coefficients, those structural paths should be removed.

# Out-of-sample predictive power
Out of sample predictive power has to be evaluated using a simplified model without HOCs as an approximation as seminr as of now does not support plspredict for HOC
If the root mean square error (RMSE) or the mean absolute deviation (MAD) of the naive LM model is below the ones for the PLS model, this indicates a lack of predictive power.

```{r plspredict, echo = FALSE}
plspre <- predict_pls(proxymodel, noFolds = 10)
sumplspre <- summary(plspre)
oospp <- (as.data.frame(sumplspre$PLS_out_of_sample) %>%
  rbind(as.data.frame(sumplspre$LM_out_of_sample)) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[1,] - (as.data.frame(sumplspre$PLS_out_of_sample))[1,]) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[2,] - (as.data.frame(sumplspre$PLS_out_of_sample))[2,])  %>%
  cbind(`Prediction Errors` = c("PLS RMSE", "PLS MAD", "LM RMSE", "LM MAD", "RMSE Difference", "MAD Difference")))[c(1,3,5,2,4,6),c(11,1:10)]
datatable(oospp,
          options = list(pageLength = nrow(oospp)),
          rownames = FALSE,
          caption = 'Out-of-sample predictive power') %>%
  formatRound(2:11,
              digits = 3) %>%
  formatStyle(names(oospp), backgroundColor = styleInterval(cuts = c(0), values = c('#ff9999', '#00')))
```
For the approximation model, only CCTB4 and CCTB6 are predicted better by the PLS model than by the linear model in terms of MAD.
This indicates that the model has low out-of-sample predictive power.

# Significance and relevance of path coefficients
Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.
```{r path-coeff, echo = FALSE}
pcbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pcbasesplit <- base::strsplit(pcbase$Construct.Rel., "  ->  ")
pcbasesplit1 <- c()
pcbasesplit2 <- c()
for (i in 1:length(pcbasesplit)){
  pcbasesplit1 <- append(pcbasesplit1, pcbasesplit[[i]][1])
  pcbasesplit2 <- append(pcbasesplit2, pcbasesplit[[i]][2])
}
pclocbase <- rownames_to_column(as.data.frame(sumbofsmo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pclocbasesplit <- base::strsplit(pclocbase$Construct.Rel., "  ->  ")
pclocbasesplit1 <- c()
pclocbasesplit2 <- c()
for (i in 1:length(pclocbasesplit)){
  pclocbasesplit1 <- append(pclocbasesplit1, pclocbasesplit[[i]][1])
  pclocbasesplit2 <- append(pclocbasesplit2, pclocbasesplit[[i]][2])
}
pcdf <- (pcbase %>% 
  mutate('Exogenous Construct' = pcbasesplit1, 
         'Endogenous Construct' = pcbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pcbase$`T Stat.`),
         p = pt(abs(pcbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pcbase$`2.5% CI` < 0 &  pcbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pcdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- (pclocbase %>% 
  mutate('Exogenous Construct' = pclocbasesplit1, 
         'Endogenous Construct' = pclocbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pclocbase$`T Stat.`),
         p = pt(abs(pclocbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pclocbase$`2.5% CI` < 0 &  pclocbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pclocdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- pclocdf %>% filter(!(`Exogenous Construct` %in% pcdf$`Exogenous Construct` & `Endogenous Construct` %in% pcdf$`Endogenous Construct`))
pcalldf <- union(pcdf, pclocdf)
datatable(pcalldf,
          filter = 'top',
          options = list(pageLength = nrow(pcalldf)),
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcalldf)[9], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.05), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```
Integrity have no significant influence on the Response Beliefs lower-constructs or on Perceived Severity.
Concerning Response Beliefs lower-order constructs, Benevolence and Competence only show a significant influence on Perceived Response Efficacy.
Threat Beliefs has no significant effect on Behavioral Intention.
All other path coefficients are significant.


# Summary table
```{r summary table-df, echo = FALSE, include = FALSE}
sumsm <- pcdf[,-c(3,5:7)] %>% 
  left_join(hocf2)  %>%
  left_join(vif %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                           'Endogenous Construct' = 'Endogenous.Construct')) %>%
  rename('Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
         '0 in Path Coefficient CI' = '0 in CI',
         'Path Coefficient p' = 'p')
colnames(sumsm)[5] <- paste0("Path Coefficient t(", nrow(model$data), ")")
```
```{r summary table-df print, echo = FALSE}
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          colnames = c("f²" = 7),
          caption = 'Structural Model Summary') %>%
  formatRound(c(3,5:8),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[5], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.05), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.02), values = c('#ff9999', '#00'))) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

# Results summary
The path from Threat Beliefs insignificant and the effect sizes are negligible.
Therefore, this path and the Threat Beliefs and Knowledge constructs can be removed from the model.
With Threat Beliefs gone, the Distrusting Beliefs lower-construct Integrity can be removed as well on the basis of its non-significant path coefficients and lack of effect on the Response Beliefs lower-order constructs.
