---
title: "Climate Crisis Model Iteration 2-d (General) Structural Model Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
# Load models and create summaries
model <- readRDS("Models/model-cc-2-d-1.RDS")
bootmodel <- readRDS("Models/model-boot-cc-2-d-1.RDS")
bootfsmodel <- readRDS("Models/model-fs-boot-cc-2-d-1.RDS")
proxymodel <- readRDS("Models/model-proxy-cc-2-d-1.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Set seminr plot theme
thm <- seminr_theme_create(construct.compositeA.arrow = "backward", construct.compositeA.use_weights = FALSE, plot.adj = FALSE)
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots
## Structural Model Only
This is a path model showing only the structural model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel)
```

# Collinearity
Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.
```{r collinearity vif, echo = FALSE}
vif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(summo$vif_antecedents)){
  x = names(summo$vif_antecedents[i])
  for (j in 1:length(summo$vif_antecedents[[{{x}}]])){
    y = names(summo$vif_antecedents[[{{x}}]])[j]
    vif <- vif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = summo$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(sumfs$vif_antecedents)){
  x = names(sumfs$vif_antecedents[i])
  for (j in 1:length(sumfs$vif_antecedents[[{{x}}]])){
    y = names(sumfs$vif_antecedents[[{{x}}]])[j]
    locvif <- locvif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = sumfs$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- locvif %>% filter(!(Exogenous.Construct %in% vif$Exogenous.Construct & Endogenous.Construct %in% vif$Endogenous.Construct))
vif <- union(vif, locvif)
datatable(vif,
          filter = 'top',
          options = list(pageLength = nrow(vif)),
          rownames = FALSE,
          colnames = c('Exogenous Construct' = 1,
                        'Endogenous Construct' = 2),
          caption = 'Results of the structural collinearity assessment') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```
There is no collinearity as indicated by VIF. Some VIF values are above 3, but still below the critical value of 5. This is mainly the case for lower-order construct relationships.

# In-sample predictive power
In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.
```{r in-sample pp r^2, echo=FALSE}
r2hoc <- data.frame(Construct = colnames(summo$paths),
                    "R^2" = summo$paths[1,],
                    "AdjR^2" = summo$paths[2,])
r2loc <- data.frame(Construct = colnames(sumfs$paths),
                    "R^2" = sumfs$paths[1,],
                    "AdjR^2" = sumfs$paths[2,]) %>%
  filter(Construct %notin% r2hoc$Construct)
r2 <- union(r2hoc, r2loc)
datatable(r2,
          filter = 'top',
          options = list(pageLength = nrow(r2)),
          rownames = FALSE,
          colnames = c('R²' = 2,
                        'R²adj' = 3),
          caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.25,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```
R² for the lower-order construct Perceived Response Costs is below the critical threshold of 0.1.
Other than that, the R²s for the lower-order construct Perceived Response Efficacy and Perceived Self-Efficacy, and for the construct Behavioral Intention are between 0.1 and 0.25, indicating very weak in-sample predictive power.
In-sample predictive power for all other constructs is weak, as all R² values remain below 0.5.

# Effect size
Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
smhoc <- data.frame(model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target)
hocf2vec <- c()
for (i in 1:nrow(smhoc)){
  x = smhoc[i,1]
  y = smhoc[i, 2]
hocf2vec <- append(hocf2vec, summo$fSquare[[{{x}},{{y}}]])  
}
hocf2 <- smhoc %>% cbind(hocf2vec) %>% rename('f^2' = 3)
smloc <- data.frame(model$first_stage_model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target) %>%
  filter('Exogenous Construct' %notin% smhoc$`Exogenous Construct`)
locf2vec <- c()
for (i in 1:nrow(smloc)){
  x = smloc[i,1]
  y = smloc[i, 2]
locf2vec <- append(locf2vec, sumfs$fSquare[[{{x}},{{y}}]])  
}
locf2 <- smloc %>% cbind(locf2vec) %>% rename('f^2' = 3) %>% 
  filter(!(`Exogenous Construct` %in% hocf2$`Exogenous Construct` & `Endogenous Construct` %in% hocf2$`Endogenous Construct`))
f2 <- union(hocf2, locf2)
datatable(f2,
          filter = 'top',
          options = list(pageLength = nrow(f2)),
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.02), values = c('#ff9999', '#00')))
```

f² indicates negligible effect sizes for many of the relationships involving lower-order constructs.
For the Distrusting Beliefs lower-order constructs, Integrity has only negligible effects, Competence only on Perceived Severity, and Benevolence none on Perceived Response Costs.
None of the Threat or Response Beliefs lower-order constructs has a discernible effect on Behavioral Intention.
On a construct level, there seems to be no discernible effect of any of the exogenous constructs on Behavioral Intention, or of Knowledge on Response Beliefs or any of its lower-order constructs.
If this is mirrored in non-significant path coefficients, those structural paths should be removed.

# Out-of-sample predictive power
Out of sample predictive power has to be evaluated using a simplified model without HOCs as an approximation as seminr as of now does not support plspredict for HOC
If the root mean square error (RMSE) or the mean absolute deviation (MAD) of the naive LM model is below the ones for the PLS model, this indicates a lack of predictive power.

```{r plspredict, echo = FALSE}
plspre <- predict_pls(proxymodel, noFolds = 10)
sumplspre <- summary(plspre)
oospp <- (as.data.frame(sumplspre$PLS_out_of_sample) %>%
  rbind(as.data.frame(sumplspre$LM_out_of_sample)) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[1,] - (as.data.frame(sumplspre$PLS_out_of_sample))[1,]) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[2,] - (as.data.frame(sumplspre$PLS_out_of_sample))[2,])  %>%
  cbind(`Prediction Errors` = c("PLS RMSE", "PLS MAD", "LM RMSE", "LM MAD", "RMSE Difference", "MAD Difference")))[c(1,3,5,2,4,6),c(11,1:10)]
datatable(oospp,
          options = list(pageLength = nrow(oospp)),
          rownames = FALSE,
          caption = 'Out-of-sample predictive power') %>%
  formatRound(2:11,
              digits = 3) %>%
  formatStyle(names(oospp), backgroundColor = styleInterval(cuts = c(0), values = c('#ff9999', '#00')))
```
For the approximation model, only CCBI1 is predicted better by the PLS model than by the linear model in terms of both RMSE and MAD.
This indicates that the model has low out-of-sample predictive power.

# Significance and relevance of path coefficients
Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.
```{r path-coeff, echo = FALSE}
pcbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pcbasesplit <- base::strsplit(pcbase$Construct.Rel., "  ->  ")
pcbasesplit1 <- c()
pcbasesplit2 <- c()
for (i in 1:length(pcbasesplit)){
  pcbasesplit1 <- append(pcbasesplit1, pcbasesplit[[i]][1])
  pcbasesplit2 <- append(pcbasesplit2, pcbasesplit[[i]][2])
}
pclocbase <- rownames_to_column(as.data.frame(sumbofsmo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pclocbasesplit <- base::strsplit(pclocbase$Construct.Rel., "  ->  ")
pclocbasesplit1 <- c()
pclocbasesplit2 <- c()
for (i in 1:length(pclocbasesplit)){
  pclocbasesplit1 <- append(pclocbasesplit1, pclocbasesplit[[i]][1])
  pclocbasesplit2 <- append(pclocbasesplit2, pclocbasesplit[[i]][2])
}
pcdf <- (pcbase %>% 
  mutate('Exogenous Construct' = pcbasesplit1, 
         'Endogenous Construct' = pcbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pcbase$`T Stat.`),
         p = pt(abs(pcbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pcbase$`2.5% CI` < 0 &  pcbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pcdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- (pclocbase %>% 
  mutate('Exogenous Construct' = pclocbasesplit1, 
         'Endogenous Construct' = pclocbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pclocbase$`T Stat.`),
         p = pt(abs(pclocbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pclocbase$`2.5% CI` < 0 &  pclocbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pclocdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- pclocdf %>% filter(!(`Exogenous Construct` %in% pcdf$`Exogenous Construct` & `Endogenous Construct` %in% pcdf$`Endogenous Construct`))
pcalldf <- union(pcdf, pclocdf)
datatable(pcalldf,
          filter = 'top',
          options = list(pageLength = nrow(pcalldf)),
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcalldf)[9], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.05), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```
As already hinted by a lack of effect size among all exogenous construct, only Response Beliefs (and its lower-order constructs Perceived Response Efficacy and Perceived REsponse Costs) show a significant influence on Behavioral Intention as indicated by the path coefficients.
The path from Knowledge to Response Beliefs and all its lower-order constructs is non-significant as well.
The paths from Integrity are non-significant except for the path to Perceived Severity, as are all paths from Competence to the Response Beliefs lower-order constructs.
The path from Benevolence to Perceived Response Costs is also non-significant.
The path from Perceived Self-Efficacy to Behavioral Intention is also non-significant.
All other path coefficients are significant.


# Summary table
```{r summary table-df, echo = FALSE, include = FALSE}
sumsm <- pcdf[,-c(3,5:7)] %>% 
  left_join(hocf2)  %>%
  left_join(vif %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                           'Endogenous Construct' = 'Endogenous.Construct')) %>%
  rename('Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
         '0 in Path Coefficient CI' = '0 in CI',
         'Path Coefficient p' = 'p')
colnames(sumsm)[5] <- paste0("Path Coefficient t(", nrow(model$data), ")")
```
```{r summary table-df print, echo = FALSE}
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          colnames = c("f²" = 7),
          caption = 'Structural Model Summary') %>%
  formatRound(c(3,5:8),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[5], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.05), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.02), values = c('#ff9999', '#00'))) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

# Results summary
The paths from Threat Beliefs, Personal Moral Norm, and Subjective Norm to Behavioral Intention are insignificant and the effect sizes are negligible.
Only the path from Response Belief is significant, although the effect sizes is small.
The paths from Knowledge to Response Beliefs are also non-significant and there are no discernible effects.
Knowledge, Threat Beliefs, Personal Moral Norm, and Subjective Norm can be removed from the model.
Concerning lower-order constructs, Perceived Self-Efficacy has no discernible effect on Behavioral Intention, and the path coefficient is insignificant.
Therefore, Perceived Self-Efficacy can be removed.
Further, the Distrusting Beliefs lower order-constructs Integrity and Competence have no discernible effect on and no significant path to any of the remaining lower-order construct.
Therefore, the Distrusting Beliefs higher-order construct can be substituted by a regular Distrusting Beliefs Benevolence construct.
