---
title: "Climate Crisis Model Iteration 2-b (Only Heating) Measurement Model Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
# Load models and create summaries
model <- readRDS("Models/model-cc-2-b.RDS")
bootmodel <- readRDS("Models/model-boot-cc-2-b.RDS")
bootfsmodel <- readRDS("Models/model-fs-boot-cc-2-b.RDS")
summo <- summary(model)
summo$fSquare
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Load redundancy analysis models
radn <- readRDS("Models/radn-cc-2-b.RDS")
rain <- readRDS("Models/rain-cc-2-b.RDS")
# Set seminr plot theme
thm <- seminr_theme_create(construct.compositeA.arrow = "backward", construct.compositeA.use_weights = FALSE, plot.adj = FALSE)
seminr_theme_set(thm)
```

# Model plots
## Original Estimate Path Model
This is the original estimate path model.
```{r plot model, echo=FALSE}
plot(model, title = "Original Estimate Model")
```

## Bootstrapped Path Model
This is the bootstrapped path model.
```{r plot bootmodel, echo=FALSE}
plot(bootmodel, title = "Bootstrapped Model")
```

## Measurement Model Only
This is a path model showing only the measurement model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel, measurement_only = TRUE)
```
```{r eval-df, echo = FALSE, include=FALSE}
# Base DF
evalmm <- data.frame(Construct = model$mmMatrix[,1],
                           Type = ifelse(grepl("HOCB", model$mmMatrix[,3]),
                                         "HOC", "Construct"),
                           Mode = dplyr::recode(model$mmMatrix[,3],
                                         "A" = "reflective",
                                         "B" = "formative",
                                         "HOCB" = "higher-order"),
                           Indicator.or.LOC = model$mmMatrix[,2])
```

# Evaluation of the reflective measurement model
```{r ref-eval prep, echo = FALSE, include=FALSE}
refevalmmbase <- evalmm %>% filter(Mode == "reflective") %>% rename(Indicator = Indicator.or.LOC) %>% 
  mutate(Type = NULL, Mode = NULL)
refloadings <- c()
for (i in 1:nrow(refevalmmbase)){
  refloadings <<- append(refloadings, sumfs$loadings[refevalmmbase$Indicator[i], refevalmmbase$Construct[i]])
}

cicr <- data.frame(Construct = row.names(sumfs$reliability), 
                   AVE = as.numeric(sumfs$reliability[,3]), 
                   Calpha = as.numeric(sumfs$reliability[,1]),
                   rhoC = as.numeric(sumfs$reliability[,2]),
                   rhoA = as.numeric(sumfs$reliability[,4]))
#Next step is HTMT
boothtmtbase <- data.frame(Construct.Rel. = row.names(sumbomo$bootstrapped_HTMT),
                          Lower.CI = as.numeric(sumbomo$bootstrapped_HTMT[,5]),
                          Upper.CI = as.numeric(sumbomo$bootstrapped_HTMT[,6])) %>%
  rbind(data.frame(Construct.Rel. = row.names(sumbofsmo$bootstrapped_HTMT),
                          Lower.CI = as.numeric(sumbofsmo$bootstrapped_HTMT[,5]),
                          Upper.CI = as.numeric(sumbofsmo$bootstrapped_HTMT[,6])))
#For HTMT evaluation, one should consider only reflective constructs and LOCs
htmtvec <- c(unique(refevalmmbase$Construct))
# Transform "Relationships" Column into two distinct columns
boothtmtsplit <- base::strsplit(boothtmtbase$Construct.Rel., "  ->  ")
boothtmtsplit1 <- c()
boothtmtsplit2 <- c()
for (i in 1:length(boothtmtsplit)){
 boothtmtsplit1 <<- append(boothtmtsplit1, boothtmtsplit[[i]][1])
 boothtmtsplit2 <<- append(boothtmtsplit2, boothtmtsplit[[i]][2])
}
boothtmt <- (boothtmtbase %>% mutate(Construct.Rel. = NULL, Construct.1 = boothtmtsplit1, Construct.2 = boothtmtsplit2))[,c(3:4,1:2)] %>%
  filter(Construct.1 %in% htmtvec & Construct.2 %in% htmtvec)
maxhtmt <- data.frame(Construct = boothtmt[,1], Max.HTMT =  boothtmt[,4]) %>% 
  rbind(data.frame(Construct = boothtmt[,2], Max.HTMT =  boothtmt[,4])) %>%
  group_by(Construct) %>%
  summarise(Max.HTMT = max(Max.HTMT)) %>%
  mutate('1.in.HTMT.CI' = ifelse(Max.HTMT >=1, TRUE, FALSE))
# Make final data frame
refevalmm <- refevalmmbase %>% cbind(Loadings = refloadings) %>% left_join(cicr) %>% left_join(maxhtmt[,c(1,3)])
```

## Convergent validity
Ideally, outer loadings (<font face="Symbol">l</font>) should be $\geq$ 0.70. Loadings below 0.40 are unacceptable. AVE should be > 0.50. 

## Internal consistency reliability
Both Cronbach's <font face="Symbol">a</font> and composite reliability <font face="Symbol">r</font><sub>c</sub> should be $\geq$ 0.60 and $\leq$ 0.90. The upper threshold of acceptability is 0.95.

## Discriminant validity
Discriminant validity is evaluated using the heterotrait-monotrait ratio (HTMT). The HTMT bootstrap confidence interval should not contain 1.

```{r ref-eval, echo=FALSE}
datatable(refevalmm,
          filter = 'top',
          options = list(pageLength = nrow(refevalmm)),
          rownames = FALSE,
          colnames = c("Loading" = 3,
                        "Cronbach\'s alpha" = 5, 
                       "Composite reliability" = 6,
                       "Construct reliability" = 7,
                       "1 in HTMT CI" = 8),
          caption = 'Results of the reflective measurement model evaluation') %>%
  formatRound(3:7,
              digits = 3) %>%
  formatStyle('Loading', backgroundColor = styleInterval(cuts = c(0.4, 0.708), values = c('#ff9999', '#ffe5e5', '#00'))) %>%
  formatStyle('AVE', backgroundColor = styleInterval(cuts = c(0.5), values = c('#ff9999', '#00'))) %>%
  formatStyle('Cronbach\'s alpha', backgroundColor = styleInterval(cuts = c(0.6,0.9,0.95,0.999), values = c('#ff9999', '#00','#ffe5e5',  '#ff9999', '#00'))) %>%
  formatStyle('Composite reliability', backgroundColor = styleInterval(cuts = c(0.6,0.9,0.95,0.999), values = c('#ff9999', '#00', '#ffe5e5', '#ff9999', '#00'))) %>%
    formatStyle('Construct reliability', backgroundColor = styleInterval(cuts = c(0.6,0.9,0.95,0.999), values = c('#ff9999', '#00','#ffe5e5',  '#ff9999', '#00'))) %>%
  formatStyle('1 in HTMT CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```
Convergent validity is established for all constructs, as is internal consistency reliability.
There seem to be HTMT issues for the Distrusting Beliefs lower-order constructs.

```{r ref-eval-HTMT,echo=FALSE}
#If there are problems with the HTMT, here is a detailed table
datatable(boothtmt,
          filter = 'top',
          options = list(pageLength = nrow(boothtmt)),
          rownames = FALSE,
          colnames = c("Construct 1" = 1,
                        "Construct 2" = 2, 
                       "Lower CI HTMT" = 3, 
                       "Upper CI HTMT" = 4),
          caption = 'Details of the bootstrapped HTMT ratios') %>%
  formatRound(3:4,
              digits = 3) %>%
    formatStyle('Lower CI HTMT', backgroundColor = styleInterval(cuts = c(0.9,1), values = c('#00', '#ffe5e5', '#ff9999'))) %>%
  formatStyle('Upper CI HTMT', backgroundColor = styleInterval(cuts = c(0.9,1), values = c('#00', '#ffe5e5', '#ff9999')))
```
As before, the HTMT bootstrap confidence intervals are only problematic for the Distrusting Beliefs lower-order constructs.
All others are below the critical thresholds.

## Results of the evaluation of the reflective measurement model
The reflective measurement model meets all quality criteria and can be retained as-is.

# Evaluation of the formative measurement model
```{r for-eval prep, echo = FALSE, include=FALSE}
forevalbase <- evalmm %>% filter(Mode == "formative") %>% rename(Indicator = Indicator.or.LOC) %>% 
  mutate(Type = NULL, Mode = NULL)
```
## Convergent validity
To evaluate convergent validity, a redundancy analysis is conducted. The path coefficient should be $\geq$ 0.70 and R² should be $\geq$ 0.50.

```{r for-eval radn, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
plot(radn, title = "Redundancy Analysis Descriptive Norm")
sumradn <- summary(radn)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvdn <- data.frame(Construct = "Descriptive Norm", 'C.V.R^2' = sumradn$paths[1], 'C.V.PC' = sumradn$paths[3])
```

```{r for-eval rain, echo=FALSE}
# Unfortunately, this has to be done partially manually
# Copy this snippet for as many formative constructs as you want to evaluate and alter it to your needs
plot(rain, title = "Redundancy Analysis Injunctive Norm")
sumrain <- summary(rain)
# For the final dataframe, you should set a custom name and put the the name of the construct
cvin <- data.frame(Construct = "Injunctive Norm", 'C.V.R^2' = sumrain$paths[1], 'C.V.PC' = sumrain$paths[3])
```

```{r for-eval cv,echo=FALSE, include=FALSE}
# put together all dataframes, this has also to be done manually
forevalci <- bind_rows(cvdn, cvin)
```

Reiterating: For sufficient convergent validity, the path coefficient should be $\geq$ 0.70 and R² should be $\geq$ 0.50.

## Collinearity
The variance inflation factor (VIF) should be < 5, ideally $\leq$ 3.

```{r for-eval col, echo = FALSE, include = FALSE}
mmvif <- data.frame(Construct = character(),
                      Indicator = character(),
                      VIF = double())
for (i in 1:length(unique(forevalbase$Construct))){
  for (j in 1:nrow(filter(forevalbase, Construct == unique(forevalbase$Construct)[i]))){
    x = unique(forevalbase$Construct)[i]
    y = (filter(forevalbase, Construct == x))[j,"Indicator"]
    mmvif <- mmvif %>% rbind(data.frame(Construct = x,
                              Indicator = y,
                              VIF = unlist(sumfs$validity$vif_items)[paste0({{x}}, ".", {{y}})]))
  }}
```

## Significance and relevance
Indicator weights should be significant (t $geq$ 1.65, bootstrapping CI does not include 0). Otherwise, the loading  <font face="Symbol">l</font> should be $\geq$ 0.50 and significant. Any positive indicator weight implies relevance.

```{r for-eval sar, echo=FALSE, include=FALSE}
# Make weights df
btwtbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_weights)) %>% rename (
  Construct.Rel. = rowname,
  Original.Est.Wt. = "Original Est.",
  Bootstrap.Mean.Wt. = "Bootstrap Mean",
  Bootstrap.SD.Wt. = "Bootstrap SD",
  T.Stat.Wt. = "T Stat.",
  Lower.Bounds.CI.Wt. = "2.5% CI",
  Upper.Bounds.CI.Wt. = "97.5% CI"
)
btwtsplit <- base::strsplit(btwtbase$Construct.Rel., "  ->  ")
btwtsplit1 <- c()
btwtsplit2 <- c()
for (i in 1:length(btwtsplit)){
  btwtsplit1 <- append(btwtsplit1, btwtsplit[[i]][1])
  btwtsplit2 <- append(btwtsplit2, btwtsplit[[i]][2])
}
btwt <- btwtbase %>%
  cbind(data.frame(Indicator = btwtsplit1, Construct = btwtsplit2)) %>%
  mutate(Construct.Rel. = NULL,
         Bootstrap.SD.Wt. = NULL,
         '0.in.Wt.CI' = ifelse(Lower.Bounds.CI.Wt. < 0 &  Upper.Bounds.CI.Wt. > 0, TRUE, FALSE),
         Lower.Bounds.CI.Wt. = NULL,
         Upper.Bounds.CI.Wt. = NULL)
# Make loadings df
btldbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_loadings)) %>% rename(
  Construct.Rel. = rowname,
  Original.Est.Ld. = "Original Est.",
  Bootstrap.Mean.Ld. = "Bootstrap Mean",
  Bootstrap.SD.Ld. = "Bootstrap SD",
  T.Stat.Ld. = "T Stat.",
  Lower.Bounds.CI.Ld. = "2.5% CI",
  Upper.Bounds.CI.Ld. = "97.5% CI"
)
btldsplit <- base::strsplit(btldbase$Construct.Rel., "  ->  ")
btldsplit1 <- c()
btldsplit2 <- c()
for (i in 1:length(btldsplit)){
  btldsplit1 <- append(btldsplit1, btldsplit[[i]][1])
  btldsplit2 <- append(btldsplit1, btldsplit[[i]][2])
}
btld <- btldbase %>%
  cbind(data.frame(Indicator = btldsplit1, Construct = btldsplit1)) %>%
  mutate(Construct.Rel. = NULL,
         Bootstrap.SD.Ld. = NULL,
         '0.in.Ld.CI' = ifelse(Lower.Bounds.CI.Ld. < 0 &  Upper.Bounds.CI.Ld. > 0, TRUE, FALSE),
         Lower.Bounds.CI.Ld. = NULL,
         Upper.Bounds.CI.Ld. = NULL)

#Make final data frame
forevalmm <- forevalbase %>% 
  left_join(forevalci) %>%
  left_join(mmvif[,2:3]) %>%
  left_join(btwt[,-5]) %>%
  left_join(btld[,-5])
colnames(forevalmm)[8] <- paste0("t(", nrow(model$data), ") (weight)")
colnames(forevalmm)[12] <- paste0("t(", nrow(model$data), ") (loading)")
```

```{r for-eval, echo=FALSE}
datatable(forevalmm,
          filter = 'top',
          options = list(pageLength = nrow(forevalmm)),
          rownames = FALSE,
          colnames = c("CV R^2" = 3,
                        "CV pc" = 4, 
                       "Weight (original estimate)" = 6, 
                       "Weight (bootstrap mean)" = 7,
                       "0 in CI (weight)" = 9,
                       "Loading (original estimate)" = 10,
                       "Loading (bootstrap mean)" = 11,
                       "0 in CI (loading)" = 13),
          caption = 'Results of the formative measurement model evaluation') %>%
  formatRound(c(3:8, 10:12),
              digits = 3) %>%
  formatStyle('CV R^2', backgroundColor = styleInterval(cuts = c(0.5), values = c('#ff9999', '#00'))) %>%
  formatStyle('CV pc', backgroundColor = styleInterval(cuts = c(0.7), values = c('#ff9999', '#00'))) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999'))) %>%
  formatStyle(colnames(forevalmm)[8], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ffe5e5', '#00'))) %>%
  formatStyle('Loading (original estimate)', backgroundColor = styleInterval(cuts = c(0.5), values = c('#ff9999', '#00'))) %>%
  formatStyle('Loading (bootstrap mean)', backgroundColor = styleInterval(cuts = c(0.5), values = c('#ff9999', '#00'))) %>%
  formatStyle(colnames(forevalmm)[12], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('0 in CI (weight)', backgroundColor = styleEqual(c(1,0), c('#ffe5e5', '#00'), default = NULL)) %>%
  formatStyle('0 in CI (loading)', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```
Convergent validity is established for both constructs and there is no collinearity.
Three weights are insignificant on the basis of the bootstrap CI (CCDN1, CCIN1 and CCIN2), however, the loadings are large enough and significant.

## Results of the evaluation of the formative measurement model
The formative measurement model meets all quality criteria and can be retained as-is.

# Evaluation of the formative higher-order constructs
```{r hoc-eval base, echo=FALSE, include=FALSE}
forhocevalbase <- evalmm %>% filter(Mode == "higher-order") %>% rename(HOC = Construct, LOC = Indicator.or.LOC) %>% 
  mutate(Type = NULL, Mode = NULL)
```

## Convergent validity
Convergent validity cannot be evaluated.

## Collinearity
The variance inflation factor (VIF) should be < 5, ideally $\leq$ 3.
```{r hoc-for-eval col, echo = FALSE, include = FALSE}
hocvif <- data.frame(HOC = character(),
                    LOC = character(),
                    VIF = double())
for (i in 1:length(unique(forhocevalbase$HOC))){
  for (j in 1:nrow(filter(forhocevalbase, HOC == unique(forhocevalbase$HOC)[i]))){
    x = unique(forhocevalbase$HOC)[i]
    y = (filter(forhocevalbase, HOC == x))[j,"LOC"]
    hocvif <- hocvif %>% rbind(data.frame(HOC = x,
                              LOC = y,
                              VIF = unlist(summo$validity$vif_items)[paste0({{x}}, ".", {{y}})]))
  }}
```

## Significance and relevance
Indicator weights should be significant (t $\geq$ 1.65, bootstrapping CI does not include 0). Otherwise, the loading  <font face="Symbol">l</font> should be $\geq$ 0.50 and significant. Any positive indicator weight implies relevance.

```{r hoc-for-eval sar, echo=FALSE, include=FALSE}
# Make weights df
bthocwtbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_weights)) %>% rename (
  Construct.Rel. = rowname,
  Original.Est.Wt. = "Original Est.",
  Bootstrap.Mean.Wt. = "Bootstrap Mean",
  Bootstrap.SD.Wt. = "Bootstrap SD",
  T.Stat.Wt. = "T Stat.",
  Lower.Bounds.CI.Wt. = "2.5% CI",
  Upper.Bounds.CI.Wt. = "97.5% CI"
)
bthocwtsplit <- base::strsplit(bthocwtbase$Construct.Rel., "  ->  ")
bthocwtsplit1 <- c()
bthocwtsplit2 <- c()
for (i in 1:length(bthocwtsplit)){
  bthocwtsplit1 <- append(bthocwtsplit1, bthocwtsplit[[i]][1])
  bthocwtsplit2 <- append(bthocwtsplit2, bthocwtsplit[[i]][2])
}
bthocwt <- bthocwtbase %>%
  cbind(data.frame(LOC = bthocwtsplit1, HOC = bthocwtsplit2)) %>%
  mutate(Construct.Rel. = NULL,
         Bootstrap.SD.Wt. = NULL,
         '0.in.Wt.CI' = ifelse(Lower.Bounds.CI.Wt. < 0 &  Upper.Bounds.CI.Wt. > 0, TRUE, FALSE),
         Lower.Bounds.CI.Wt. = NULL,
         Upper.Bounds.CI.Wt. = NULL)
# Make loadings df
bthocldbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_loadings)) %>% rename(
  Construct.Rel. = rowname,
  Original.Est.Ld. = "Original Est.",
  Bootstrap.Mean.Ld. = "Bootstrap Mean",
  Bootstrap.SD.Ld. = "Bootstrap SD",
  T.Stat.Ld. = "T Stat.",
  Lower.Bounds.CI.Ld. = "2.5% CI",
  Upper.Bounds.CI.Ld. = "97.5% CI"
)
bthocldsplit <- base::strsplit(bthocldbase$Construct.Rel., "  ->  ")
bthocldsplit1 <- c()
bthocldsplit2 <- c()
for (i in 1:length(bthocldsplit)){
  bthocldsplit1 <- append(bthocldsplit1, bthocldsplit[[i]][1])
  bthocldsplit2 <- append(bthocldsplit1, bthocldsplit[[i]][2])
}
bthocld <- btldbase %>%
  cbind(data.frame(LOC = btldsplit1, HOC = btldsplit1)) %>%
  mutate(Construct.Rel. = NULL,
         Bootstrap.SD.Ld. = NULL,
         '0.in.Ld.CI' = ifelse(Lower.Bounds.CI.Ld. < 0 &  Upper.Bounds.CI.Ld. > 0, TRUE, FALSE),
         Lower.Bounds.CI.Ld. = NULL,
         Upper.Bounds.CI.Ld. = NULL)

#Make final data frame
forhocevalmm <- forhocevalbase %>%
  left_join(hocvif[,2:3]) %>%
  left_join(bthocwt[,-5]) %>%
  left_join(bthocld[,-5])
colnames(forhocevalmm)[6] <- paste0("t(", nrow(model$data), ") (weight)")
colnames(forhocevalmm)[10] <- paste0("t(", nrow(model$data), ") (loading)")
```
```{r hoc-for-eval, echo=FALSE}
datatable(forhocevalmm,
          filter = 'top',
          options = list(pageLength = nrow(forhocevalmm)),
          rownames = FALSE,
          colnames = c("Weight (original estimate)" = 4, 
                       "Weight (bootstrap mean)" = 5,
                       "0 in CI (weight)" = 7,
                       "Loading (original estimate)" = 8,
                       "Loading (bootstrap mean)" = 9,
                       "0 in CI (loading)" = 11),
          caption = 'Results of the formative higher-order construct evaluation') %>%
  formatRound(c(3:6, 8:10),
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999'))) %>%
  formatStyle(colnames(forhocevalmm)[6], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ffe5e5', '#00'))) %>%
  formatStyle('Loading (original estimate)', backgroundColor = styleInterval(cuts = c(0.5), values = c('#ff9999', '#00'))) %>%
  formatStyle('Loading (bootstrap mean)', backgroundColor = styleInterval(cuts = c(0.5), values = c('#ff9999', '#00'))) %>%
  formatStyle(colnames(forhocevalmm)[10], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('0 in CI (weight)', backgroundColor = styleEqual(c(1,0), c('#ffe5e5', '#00'), default = NULL)) %>%
  formatStyle('0 in CI (loading)', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```

The VIFs for the Distrusting Beliefs are above 3, but still below 5.
With that, there are no issues with collinearity.
The weight for Injunctive norm is not significant, and the loading is too small. Therefore it has to be discarded.
All other weights are significant and relevant.

## Results of the formative higher-order constructs evaluation
The formative higher-order constructs can be retained as-is.

# Results summary
The reflective and formative measurement model meet the quality criteria.
The lower-order construct Injunctive Norm has to be deleted.
With that, Descriptive Norm substitutes the Subjective Norm construct.
