---
title: "Template Structural Model Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
# Load models and create summaries
model <- readRDS("Models/model-cc-3-a.RDS")
bootmodel <- readRDS("Models/model-boot-cc-3-a.RDS")
bootfsmodel <- readRDS("Models/model-fs-boot-cc-3-a.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Set seminr plot theme
thm <- seminr_theme_create(construct.compositeA.arrow = "backward", construct.compositeA.use_weights = FALSE, plot.adj = FALSE)
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots
## Structural Model Only
This is a path model showing only the structural model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel, structure_only = TRUE)
```

# Collinearity
Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.
```{r collinearity vif, echo = FALSE}
vif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(summo$vif_antecedents)){
  x = names(summo$vif_antecedents[i])
  for (j in 1:length(summo$vif_antecedents[[{{x}}]])){
    y = names(summo$vif_antecedents[[{{x}}]])[j]
    vif <- vif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = summo$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(sumfs$vif_antecedents)){
  x = names(sumfs$vif_antecedents[i])
  for (j in 1:length(sumfs$vif_antecedents[[{{x}}]])){
    y = names(sumfs$vif_antecedents[[{{x}}]])[j]
    locvif <- locvif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = sumfs$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- locvif %>% filter(!(Exogenous.Construct %in% vif$Exogenous.Construct & Endogenous.Construct %in% vif$Endogenous.Construct))
vif <- union(vif, locvif)
datatable(vif,
          filter = 'top',
          options = list(pageLength = nrow(vif)),
          rownames = FALSE,
          colnames = c('Exogenous Construct' = 1,
                        'Endogenous Construct' = 2),
          caption = 'Results of the structural collinearity assessment') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

The VIF is not above 5 for any combination of constructs, however, there are some issues concerning the VIFs for many LOCs with Integrity approaching 5 for all its endogenous LOCs.

# In-sample predictive power
In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.
```{r in-sample pp r^2, echo=FALSE}
r2hoc <- data.frame(Construct = colnames(summo$paths),
                    "R^2" = summo$paths[1,],
                    "AdjR^2" = summo$paths[2,])
r2loc <- data.frame(Construct = colnames(sumfs$paths),
                    "R^2" = sumfs$paths[1,],
                    "AdjR^2" = sumfs$paths[2,]) %>%
  filter(Construct %notin% r2hoc$Construct)
r2 <- union(r2hoc, r2loc)
datatable(r2,
          filter = 'top',
          options = list(pageLength = nrow(r2)),
          rownames = FALSE,
          colnames = c('R²' = 2,
                        'R²adj' = 3),
          caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.25,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```
R² is below the threshold for Perceived Response Costs and quite low for Perceived Self-Efficacy and Perceived Response Efficacy.

# Effect size
Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
smhoc <- data.frame(model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target)
hocf2vec <- c()
for (i in 1:nrow(smhoc)){
  x = smhoc[i,1]
  y = smhoc[i, 2]
hocf2vec <- append(hocf2vec, summo$fSquare[[{{x}},{{y}}]])  
}
hocf2 <- smhoc %>% cbind(hocf2vec) %>% rename('f^2' = 3)
smloc <- data.frame(model$first_stage_model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target) %>%
  filter('Exogenous Construct' %notin% smhoc$`Exogenous Construct`)
locf2vec <- c()
for (i in 1:nrow(smloc)){
  x = smloc[i,1]
  y = smloc[i, 2]
locf2vec <- append(locf2vec, sumfs$fSquare[[{{x}},{{y}}]])  
}
locf2 <- smloc %>% cbind(locf2vec) %>% rename('f^2' = 3) %>% 
  filter(!(`Exogenous Construct` %in% hocf2$`Exogenous Construct` & `Endogenous Construct` %in% hocf2$`Endogenous Construct`))
f2 <- union(hocf2, locf2)
datatable(f2,
          filter = 'top',
          options = list(pageLength = nrow(f2)),
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.02), values = c('#ff9999', '#00')))
```

Effect sizes are negligible for many LOC-LOC paths. In detail:
Knowledge has only a negligible effect on the Response Beliefs HOC overall, as on any of its LOCs.
Distrusting Beliefs overall has a medium effect on Response Beliefs and a large effect on Threat Beliefs.
DB Benevolence has only a negligible effect on PRC and a very weak effect on PSUS. It has a weak effect on all other LOCs.
DB Competence has a negligible effect on all LOCs buth PSE, on which it has a weak effect.
DB Integrity has a negligible effect on all LOCs.
This begs the question on how overall, Distrusting Beliefs has a medium to large effect on the other HOCs.
Response Beliefs overall has a weak effect on Behavioral Intention.
PRC and PRE have a negligible effect, while PSE has a weak effect.
Threat Beliefs has only a negligible effect on Behavioral Intention, as have its LOCs.
Personal Moral Norm has a weak effect on Behavioral Intention.
Subjective Norm has a weak effect on Behavioral Intention. Injunctive Norm has a negligible effect, while Descriptive Norm has a weak effect.

# Out-of-sample predictive power
Out of sample predictive power cannot be valuated using R, simplePLS seems to be deprecated.

# Significance and relevance of path coefficients
Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.
```{r path-coeff, echo = FALSE}
pcbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pcbasesplit <- base::strsplit(pcbase$Construct.Rel., "  ->  ")
pcbasesplit1 <- c()
pcbasesplit2 <- c()
for (i in 1:length(pcbasesplit)){
  pcbasesplit1 <- append(pcbasesplit1, pcbasesplit[[i]][1])
  pcbasesplit2 <- append(pcbasesplit2, pcbasesplit[[i]][2])
}
pclocbase <- rownames_to_column(as.data.frame(sumbofsmo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pclocbasesplit <- base::strsplit(pclocbase$Construct.Rel., "  ->  ")
pclocbasesplit1 <- c()
pclocbasesplit2 <- c()
for (i in 1:length(pclocbasesplit)){
  pclocbasesplit1 <- append(pclocbasesplit1, pclocbasesplit[[i]][1])
  pclocbasesplit2 <- append(pclocbasesplit2, pclocbasesplit[[i]][2])
}
pcdf <- (pcbase %>% 
  mutate('Exogenous Construct' = pcbasesplit1, 
         'Endogenous Construct' = pcbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pcbase$`T Stat.`),
         p = pt(abs(pcbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pcbase$`2.5% CI` < 0 &  pcbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pcdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- (pclocbase %>% 
  mutate('Exogenous Construct' = pclocbasesplit1, 
         'Endogenous Construct' = pclocbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pclocbase$`T Stat.`),
         p = pt(abs(pclocbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pclocbase$`2.5% CI` < 0 &  pclocbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pclocdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- pclocdf %>% filter(!(`Exogenous Construct` %in% pcdf$`Exogenous Construct` & `Endogenous Construct` %in% pcdf$`Endogenous Construct`))
pcalldf <- union(pcdf, pclocdf)
datatable(pcalldf,
          filter = 'top',
          options = list(pageLength = nrow(pcalldf)),
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcalldf)[9], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.05), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```

Concerning significance and relevance of path coefficients, again, the paths for many LOC-LOC relationships are insignificant.
In detail:
The paths from Knowledge to the RB LOCs are insignificant on the basis of both CI and t, except for PSE where it is only insignificant on the basis of CI. The path to RB itself, however, is significant.
The paths from Knowledge to Threat Beliefs as well as its LOCs are all significant.
All paths from Distrusting Beliefs are significant.
From DB Benevolence, only the path to PRC is insignificant.
From DB Competence, only the paths to the TB LOCs are significant.
From DB Integrity, only the paths to the TB LOCs are significant.
The path from Response Beliefs to Behavioral Intention is significant. However, in the LOCs the path from PRC is insignificant.
The path from Threat Beliefs to Behavioral Intention is insignificant on the basis of the CI, but significant on the basis of t. The path from Perceived Severity is insignificant, the path from Perceived Susceptibility is is significant.
The path from Personal Moral Norm to Behavioral Intention is significant.
So is the path from Subjective Norm, but the path from the Injunctive Norm LOC is insignificant.

# Summary table
```{r summary table-df, echo = FALSE, include = FALSE}
sumsm <- pcdf[,-c(3,5:7)] %>% 
  left_join(hocf2)  %>%
  left_join(vif %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                           'Endogenous Construct' = 'Endogenous.Construct')) %>%
  rename('Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
         '0 in Path Coefficient CI' = '0 in CI',
         'Path Coefficient p' = 'p')
colnames(sumsm)[5] <- paste0("Path Coefficient t(", nrow(model$data), ")")
```
```{r summary table-df print, echo = FALSE}
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          colnames = c("f²" = 7),
          caption = 'Structural Model Summary') %>%
  formatRound(c(3,5:8),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[5], backgroundColor = styleInterval(cuts = c(1.65), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.05), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.02), values = c('#ff9999', '#00'))) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

# Results summary
To sum up, the path from Threat Beliefs to Behavioral Intention is insignificant on the basis of the Bootstrapping confidence interval and has only a negligible effect effect. With that, Threat Beliefs can be deleted from  the model.
Knowledge has only a negligible effect on Response Beliefs, but a significant path coefficient. Therefore, it can be retained.
Further, on the LOC level, Injunctive Norm can possibly be deleted, making Descriptive Norm a regular construct instead of Subjective Norm.
With Threat Beliefs gone, the Distrusting Beliefs Competence and Integrity Subconstructs can possibly be deleted, making Distrusting Beliefs Benevolence a regular constructs instead of Distrusting Beliefs.
Alternatively, Distrusting Beliefs and Response Beliefs could be split up and a new model could be estimated.
