---
title: "COVID-19 Model Iteration 2 Endogeneity Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(nortest)
library(car)
# Load models and create summaries
# Load PLS Model
model <- readRDS("Models/model-co-2.RDS")
bootmodel <- readRDS("Models/model-boot-co-2.RDS")
# Load bootstrapped first stage PLS model
bootfsmodel <- readRDS("Models/model-fs-boot-co-2.RDS")
# Load approximation PLS model (no HOCs, data formatted as data.frame)
proxymodel <- readRDS("Models/model-proxy-co-2.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
sumprmo <- summary(proxymodel)
# # Bootstrap proxy model (500 samples) for comparability
# bootprmodel <- bootstrap_model(proxymodel)
# sumboprmo <- summary(bootprmodel)
# Function for Gaussian Capula Approach
createCopula <- function(P){
	H.p <- stats::ecdf(P)
	H.p <- H.p(P)
	H.p <- ifelse(H.p==0,0.0000001,H.p)
	H.p <- ifelse(H.p==1,0.9999999,H.p)
	U.p <- H.p
	p.star <- stats::qnorm(U.p)
	return(p.star)	
}
bootstrappedSignificance <- function(dataset, bootstrapresults, numIndependentVariables, numCopulas){
	for (i in 1:nrow(summary(bootstrapresults))){
		t <- summary(bootstrapresults)[i, "original"] / summary(bootstrapresults)[i, "bootSE"]
		# df = n (number of observations) - k (number of independent variables + copulas) - 1
		pvalue <- 2 * pt(-abs(t),df=nrow(dataset)-numIndependentVariables-numCopulas-1)
		cat("Pr(>|t|)", rownames(summary(bootstrapresults))[i], ": ", pvalue, "\n")
	}
}
bootSig <- function(dataset, bootstrapresults, numIndependentVariables, numCopulas){
  bootSigvec <- vector("double", length = length(numIndependentVariables + 1))
	for (i in 1:nrow(summary(bootstrapresults))){
	  t <- summary(bootstrapresults)[i, "original"] / summary(bootstrapresults)[i, "bootSE"]
		# df = n (number of observations) - k (number of independent variables + copulas) - 1
		bootSigvec[i] <- 2 * pt(-abs(t),df=nrow(dataset)-numIndependentVariables-numCopulas-1)
	}
  return(bootSigvec)
}
```
The code for the assessment of endogeneity using the Gaussian Copula approach comes from

Hult, G. T. M., J. F. Hair, D. Proksch, M. Sarstedt, A. Pinkwart, & C. M. Ringle (2018).
Addressing Endogeneity in International Marketing Applications of Partial Least Squares Structural Equation Modeling. Journal of International Marketing, 26(3), 1–21. https://doi.org/10.1509/jim.17.0151


# Test of non-normality
The Gaussian Copula approach can only be used if the independent variable in question is non-normally distributed.
```{r}
# Find out if independent (i.e., exogenous) variables are non-normally distributed
# If yes, Gaussian Copula approach can be used.
#Distrusting Beliefs
shapiro.test(model$construct_scores[,"Distrusting Beliefs"])
lillie.test(model$construct_scores[,"Distrusting Beliefs"])
ggplot(as.data.frame(model$construct_scores), aes(`Distrusting Beliefs`)) +
  geom_density()
# Knowledge
shapiro.test(model$construct_scores[,"Knowledge"])
lillie.test(model$construct_scores[,"Knowledge"])
ggplot(as.data.frame(model$construct_scores), aes(`Knowledge`)) +
  geom_density()
# Response Beliefs
shapiro.test(model$construct_scores[,"Response Beliefs"])
lillie.test(model$construct_scores[,"Response Beliefs"])
ggplot(as.data.frame(model$construct_scores), aes(`Response Beliefs`)) +
  geom_density()
# Threat Beliefs
shapiro.test(model$construct_scores[,"Threat Beliefs"])
lillie.test(model$construct_scores[,"Threat Beliefs"])
ggplot(as.data.frame(model$construct_scores), aes(`Threat Beliefs`)) +
  geom_density()
# Personal Moral Norm
shapiro.test(model$construct_scores[,"Personal Moral Norm"])
lillie.test(model$construct_scores[,"Personal Moral Norm"])
ggplot(as.data.frame(model$construct_scores), aes(`Personal Moral Norm`)) +
  geom_density()
# Subjective Norm
shapiro.test(model$construct_scores[,"Subjective Norm"])
lillie.test(model$construct_scores[,"Subjective Norm"])
ggplot(as.data.frame(model$construct_scores), aes(`Subjective Norm`)) +
  geom_density()
```
All independent (or endogenous) variables are non-normally distributed.
Therefore, the Gaussian Copula approach can be used for all of them.


# Regression of Response Beliefs on Distrusting Beliefs and Knowledge
```{r gca rb}
# Define Variables for easy access
KN <- model$construct_scores[,"Knowledge"]
DI <- model$construct_scores[,"Distrusting Beliefs"]
RB <- model$construct_scores[,"Response Beliefs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 100

# Estimate regression model
rbmodel <- lm(RB ~ DI + KN)
summary(rbmodel)
bootrb <- Boot(rbmodel, R=bootrounds)
summary(bootrb)

# Make base df
rbdf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootrb)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootrb, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables
KN_star <- createCopula(KN)
DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladirb <- lm(RB ~ DI + KN + DI_star + 0)
summary(copuladirb)
# Bootstrap Standard Errors
bootcopuladirb <- Boot(copuladirb, R=bootrounds)
summary(bootcopuladirb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladirb, 2,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladirb)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulaknrb <- lm(RB ~ DI + KN + KN_star + 0)
summary(copulaknrb)
# Bootstrap Standard Errors
bootcopulaknrb <- Boot(copulaknrb, R=bootrounds)
summary(bootcopulaknrb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaknrb, 2,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulaknrb)[1:2,5], NA, summary(bootcopulaknrb)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 2,1)[1:2], NA, bootSig(model$data, bootcopuladirb, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladiknrb <- lm(RB ~ DI + KN + DI_star + KN_star + 0)
summary(copuladiknrb)
# Bootstrap Standard Errors
bootcopuladiknrb <- Boot(copuladiknrb, R=bootrounds)
summary(bootcopuladiknrb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladiknrb, 2, 2)
# Attach to df
rbdf <- rbdf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladiknrb)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladiknrb, 2, 2))
)
datatable(rbdf) %>%
  formatRound(-1,
              digits = 3)
```
Neither the Distrusting Beliefs nor the Knowlede Copula is significant, indicating that there is no hidden endogeneity in the regression of Response Beliefs on its predictors.

# Regression of Threat Beliefs on Distrusting Beliefs and Knowledge
```{r gca tb}
# Define Variables for easy access
TB <- model$construct_scores[,"Threat Beliefs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 100

# Estimate regression model
tbmodel <- lm(TB ~ DI + KN)
summary(tbmodel)
boottb <- Boot(tbmodel, R=bootrounds)
summary(boottb)

# Make base df
tbdf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootrb)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootrb, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables - already happened
# KN_star <- createCopula(KN)
# DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladitb <- lm(TB ~ DI + KN + DI_star + 0)
summary(copuladitb)
# Bootstrap Standard Errors
bootcopuladitb <- Boot(copuladitb, R=bootrounds)
summary(bootcopuladitb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladitb, 2,1)
# Attach to df
tbdf <- tbdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladitb)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladitb, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulakntb <- lm(TB ~ DI + KN + KN_star + 0)
summary(copulakntb)
# Bootstrap Standard Errors
bootcopulakntb <- Boot(copulakntb, R=bootrounds)
summary(bootcopulakntb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulakntb, 2,1)
# Attach to df
tbdf <- tbdf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulakntb)[1:2,5], NA, summary(bootcopulakntb)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopuladitb, 2,1)[1:2], NA, bootSig(model$data, bootcopuladitb, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladikntb <- lm(TB ~ DI + KN + DI_star + KN_star + 0)
summary(copuladikntb)
# Bootstrap Standard Errors
bootcopuladikntb <- Boot(copuladikntb, R=bootrounds)
summary(bootcopuladikntb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladikntb, 2, 2)
# Attach to df
tbdf <- tbdf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladikntb)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladikntb, 2, 2))
)
datatable(tbdf) %>%
  formatRound(-1,
              digits = 3)
```
Neither the Distrusting Beliefs nor the Knowledge Copula is significant, indicating that there is no hidden endogeneity in the regression of Threat Beliefs on its predictors.

# Regression of Behavioral Intention on its predictors
```{r gca bi}
# Define Variables for easy access
BI <- model$construct_scores[,"Behavioral Intention"]
PN <- model$construct_scores[,"Personal Moral Norm"]
SN <- model$construct_scores[,"Subjective Norm"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 100

# Estimate regression model
bimodel <- lm(BI ~ RB + TB + PN + SN)
summary(bimodel)
bootbi <- Boot(bimodel, R=bootrounds)
summary(bootbi)

# Make base df
bidf <- data.frame(Construct = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm", "Copula Response Beliefs", "Copula Threat Beliefs", "Copula Personal Moral Norm", "Copula Subjective Norm"), 
                   Original.Model.Value = c(summary(bootbi)[2:5,5],NA,NA,NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootbi, 4, 0)[2:5],NA,NA,NA,NA)
)

# Calculate copulas for independent variables - already happened
RB_star <- createCopula(RB)
TB_star <- createCopula(TB)
PN_star <- createCopula(PN)
SN_star <- createCopula(SN)

# Calculate results with copula for Response Beliefs
# Input is regular model + copula + 0
copularbbi <- lm(BI ~ RB + TB + PN + SN + RB_star + 0)
summary(copularbbi)
# Bootstrap Standard Errors
bootcopularbbi <- Boot(copularbbi)
summary(bootcopularbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  RB.Co.Model.Value = c(summary(bootcopularbbi)[,5], NA, NA, NA),
  RB.Co.Model.p = c(bootSig(model$data, bootcopularbbi, 4,1), NA, NA, NA)
)

# Calculate results with copula for Threat Beliefs
# Input is regular model + copula + 0
copulatbbi <- lm(BI ~ RB + TB + PN + SN + TB_star + 0)
summary(copulatbbi)
# Bootstrap Standard Errors
bootcopulatbbi <- Boot(copulatbbi)
summary(bootcopulatbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  TB.Co.Model.Value = c(summary(bootcopulatbbi)[1:4,5], NA, summary(bootcopulatbbi)[5,5],  NA, NA),
  TB.Co.Model.p = c(bootSig(model$data, bootcopulatbbi, 4,1)[1:4], NA, bootSig(model$data, bootcopulatbbi, 4,1)[5], NA, NA)
)

# Calculate results with copula for Personal Moral Norm
# Input is regular model + copula + 0
copulapnbi <- lm(BI ~ RB + TB + PN + SN + PN_star + 0)
summary(copulapnbi)
# Bootstrap Standard Errors
bootcopulapnbi <- Boot(copulapnbi)
summary(bootcopulapnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapnbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  PN.Co.Model.Value = c(summary(bootcopulapnbi)[1:4,5], NA, NA, summary(bootcopulapnbi)[5,5],  NA),
  PN.Co.Model.p = c(bootSig(model$data, bootcopulapnbi, 4,1)[1:4], NA,  NA, bootSig(model$data, bootcopulapnbi, 4,1)[5],NA)
)

# Calculate results with copula for Subjective Norm
# Input is regular model + copula + 0
copulasnbi <- lm(BI ~ RB + TB + PN + SN + SN_star + 0)
summary(copulasnbi)
# Bootstrap Standard Errors
bootcopulasnbi <- Boot(copulasnbi)
summary(bootcopulasnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulasnbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  SN.Co.Model.Value = c(summary(bootcopulasnbi)[1:4,5], NA, NA, NA, summary(bootcopulasnbi)[5,5]),
  SN.Co.Model.p = c(bootSig(model$data, bootcopulasnbi, 4,1)[1:4], NA,  NA, NA, bootSig(model$data, bootcopulasnbi, 4,1)[5])
)

# Calculate results with copula for Response Beliefs and Threat Beliefs
# Input is regular model + copula + 0
copularbtbbi <- lm(BI ~ RB + TB + PN + SN + RB_star + TB_star + 0)
summary(copularbtbbi)
# Bootstrap Standard Errors
bootcopularbtbbi <- Boot(copularbtbbi)
summary(bootcopularbtbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.Co.Model.Value = c(summary(bootcopularbtbbi)[,5], NA, NA),
  RB.TB.Co.Model.p = c(bootSig(model$data, bootcopularbtbbi, 4,2), NA, NA)
)

# Calculate results with copula for Response Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copularbpnbi <- lm(BI ~ RB + TB + PN + SN + RB_star + PN_star + 0)
summary(copularbpnbi)
# Bootstrap Standard Errors
bootcopularbpnbi <- Boot(copularbpnbi)
summary(bootcopularbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbpnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  RB.PN.Co.Model.Value = c(summary(bootcopularbpnbi)[1:5,5], NA, summary(bootcopularbpnbi)[6,5], NA),
  RB.PN.Co.Model.p = c(bootSig(model$data, bootcopularbpnbi, 4,2)[1:5], NA, bootSig(model$data, bootcopularbpnbi, 4,2)[6], NA)
)

# Calculate results with copula for Response Beliefs and Subjective Norm
# Input is regular model + copula + 0
copularbsnbi <- lm(BI ~ RB + TB + PN + SN + RB_star + SN_star + 0)
summary(copularbsnbi)
# Bootstrap Standard Errors
bootcopularbsnbi <- Boot(copularbsnbi)
summary(bootcopularbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbsnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  RB.SN.Co.Model.Value = c(summary(bootcopularbsnbi)[1:5,5], NA, NA, summary(bootcopularbsnbi)[6,5]),
  RB.SN.Co.Model.p = c(bootSig(model$data, bootcopularbsnbi, 4,2)[1:5], NA, NA, bootSig(model$data, bootcopularbsnbi, 4,2)[6])
)

# Calculate results with copula for Threat Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copulatbpnbi <- lm(BI ~ RB + TB + PN + SN + TB_star + PN_star + 0)
summary(copulatbpnbi)
# Bootstrap Standard Errors
bootcopulatbpnbi <- Boot(copulatbpnbi)
summary(bootcopulatbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbpnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  TB.PN.Co.Model.Value = c(summary(bootcopulatbpnbi)[1:4,5], NA, summary(bootcopulatbpnbi)[5:6,5], NA),
  TB.PN.Co.Model.p = c(bootSig(model$data, bootcopulatbpnbi, 4,2)[1:4], NA, bootSig(model$data, bootcopulatbpnbi, 4,2)[5:6], NA)
)

# Calculate results with copula for Threat Beliefs and Subjective Norm
# Input is regular model + copula + 0
copulatbsnbi <- lm(BI ~ RB + TB + PN + SN + TB_star + SN_star + 0)
summary(copulatbsnbi)
# Bootstrap Standard Errors
bootcopulatbsnbi <- Boot(copulatbsnbi)
summary(bootcopulatbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbsnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  TB.SN.Co.Model.Value = c(summary(bootcopulatbsnbi)[1:4,5], NA, summary(bootcopulatbsnbi)[5,5], NA, summary(bootcopulatbsnbi)[6,5]),
  TB.SN.Co.Model.p = c(bootSig(model$data, bootcopulatbsnbi, 4,2)[1:4], NA, bootSig(model$data, bootcopulatbsnbi, 4,2)[6], NA, bootSig(model$data, bootcopulatbsnbi, 4,2)[6])
)

# Calculate results with copula for Personal Moral Norm and Subjective Norm
# Input is regular model + copula + 0
copulapnsnbi <- lm(BI ~ RB + TB + PN + SN + PN_star + SN_star + 0)
summary(copulapnsnbi)
# Bootstrap Standard Errors
bootcopulapnsnbi <- Boot(copulapnsnbi)
summary(bootcopulapnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapnsnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PN.SN.Co.Model.Value = c(summary(bootcopulapnsnbi)[1:4,5], NA, NA, summary(bootcopulapnsnbi)[5:6,5]),
  PN.SN.Co.Model.p = c(bootSig(model$data, bootcopulapnsnbi, 4,2)[1:4], NA, NA, bootSig(model$data, bootcopulapnsnbi, 4,2)[5:6])
)

# Calculate results with copula for Response Beliefs, Threat Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copularbtbpnbi <- lm(BI ~ RB + TB + PN + SN + RB_star + TB_star + PN_star + 0)
summary(copularbtbpnbi)
# Bootstrap Standard Errors
bootcopularbtbpnbi <- Boot(copularbtbpnbi)
summary(bootcopularbtbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbpnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.PN.Co.Model.Value = c(summary(bootcopularbtbpnbi)[,5], NA),
  RB.TB.PN.Co.Model.p = c(bootSig(model$data, bootcopularbtbpnbi, 4,3), NA)
)

# Calculate results with copula for Response Beliefs, Threat Beliefs and Subjective Norm
# Input is regular model + copula + 0
copularbtbsnbi <- lm(BI ~ RB + TB + PN + SN + RB_star + TB_star + SN_star + 0)
summary(copularbtbsnbi)
# Bootstrap Standard Errors
bootcopularbtbsnbi <- Boot(copularbtbsnbi)
summary(bootcopularbtbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbsnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.SN.Co.Model.Value = c(summary(bootcopularbtbsnbi)[1:6,5], NA, summary(bootcopularbtbsnbi)[7,5]),
  RB.TB.SN.Co.Model.p = c(bootSig(model$data, bootcopularbtbsnbi, 4,3)[1:6], NA, bootSig(model$data, bootcopularbtbsnbi, 4,3)[7])
)

# Calculate results with copula for Response Beliefs, Personal Moral Norm and Subjective Norm
# Input is regular model + copula + 0
copularbpnsnbi <- lm(BI ~ RB + TB + PN + SN + RB_star + PN_star + SN_star + 0)
summary(copularbpnsnbi)
# Bootstrap Standard Errors
bootcopularbpnsnbi <- Boot(copularbpnsnbi)
summary(bootcopularbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbpnsnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  RB.PN.SN.Co.Model.Value = c(summary(bootcopularbpnsnbi)[1:5,5], NA, summary(bootcopularbpnsnbi)[6:7,5]),
  RB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopularbpnsnbi, 4,3)[1:5], NA, bootSig(model$data, bootcopularbpnsnbi, 4,3)[6:7])
)

# Calculate results with copula for Threat Beliefs, Personal Moral Norm and Subjective Norm
# Input is regular model + copula + 0
copulatbpnsnbi <- lm(BI ~ RB + TB + PN + SN + TB_star + PN_star + SN_star + 0)
summary(copulatbpnsnbi)
# Bootstrap Standard Errors
bootcopulatbpnsnbi <- Boot(copulatbpnsnbi)
summary(bootcopulatbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbpnsnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  TB.PN.SN.Co.Model.Value = c(summary(bootcopulatbpnsnbi)[1:4,5], NA, summary(bootcopulatbpnsnbi)[5:7,5]),
  TB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopulatbpnsnbi, 4,3)[1:4], NA, bootSig(model$data, bootcopulatbpnsnbi, 4,3)[5:7])
)

# Calculate results with copula for Response Beliefs, Threat Beliefs, Personal Moral Norm and Subjective Norm
# Input is regular model + copula + 0
copularbtbpnsnbi <- lm(BI ~ RB + TB + PN + SN + RB_star + TB_star + PN_star + SN_star + 0)
summary(copularbtbpnsnbi)
# Bootstrap Standard Errors
bootcopularbtbpnsnbi <- Boot(copularbtbpnsnbi)
summary(bootcopularbtbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbpnsnbi, 4,4)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.PN.SN.Co.Model.Value = c(summary(bootcopularbtbpnsnbi)[,5]),
  RB.TB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopularbtbpnsnbi, 4,4))
)

datatable(bidf) %>%
  formatRound(-1,
              digits = 3)
```

In looking only at single copulas, none of copulas achieves a significant p-value.
However, when combining multiple copulas, the copula for Response Beliefs achieves a significant p-value in some cases (p < 0.1).
Further, adding the copula increases the path coefficient by 0.064 from 0.485 in the original model to 0.549.
Both of this indicates that Response Beliefs might be endogenous.
There is nothing pointing to hidden endogeneity in any of the other predictors.
