---
title: "COVID-19 Model Iteration 2 Structural Model Evaluation"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(distill)
# Load models and create summaries
# Load PLS Model
model <- readRDS("Models/model-co-2.RDS")
bootmodel <- readRDS("Models/model-boot-co-2.RDS")
# Load bootstrapped first stage PLS model
bootfsmodel <- readRDS("Models/model-fs-boot-co-2.RDS")
# Load approximation PLS model (no HOCs, data formatted as data.frame)
proxymodel <- readRDS("Models/model-proxy-co-2.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Set seminr plot theme
thm <- seminr_theme_create(construct.compositeA.arrow = "backward", construct.compositeA.use_weights = FALSE, plot.adj = FALSE)
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots

## Structural Model Only

This is a path model showing only the structural model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel, structure_only = TRUE)
```

# Collinearity

Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.

```{r collinearity vif, echo = FALSE}
vif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(summo$vif_antecedents)){
  x = names(summo$vif_antecedents[i])
  for (j in 1:length(summo$vif_antecedents[[{{x}}]])){
    y = names(summo$vif_antecedents[[{{x}}]])[j]
    vif <- vif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = summo$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(sumfs$vif_antecedents)){
  x = names(sumfs$vif_antecedents[i])
  for (j in 1:length(sumfs$vif_antecedents[[{{x}}]])){
    y = names(sumfs$vif_antecedents[[{{x}}]])[j]
    locvif <- locvif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = sumfs$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- locvif %>% filter(!(Exogenous.Construct %in% vif$Exogenous.Construct & Endogenous.Construct %in% vif$Endogenous.Construct))
vif <- union(vif, locvif)
datatable(vif,
          filter = 'top',
          options = list(pageLength = nrow(vif)),
          rownames = FALSE,
          colnames = c('Exogenous Construct' = 1,
                        'Endogenous Construct' = 2),
          caption = 'Results of the structural collinearity assessment') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```
VIF is above 3 for some constructs, specifically lower-order constructs.
But it is not above 5 for any constructs.

# In-sample predictive power
In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.
```{r in-sample pp r^2, echo=FALSE}
r2hoc <- data.frame(Construct = colnames(summo$paths),
                    "R^2" = summo$paths[1,],
                    "AdjR^2" = summo$paths[2,])
r2loc <- data.frame(Construct = colnames(sumfs$paths),
                    "R^2" = sumfs$paths[1,],
                    "AdjR^2" = sumfs$paths[2,]) %>%
  filter(Construct %notin% r2hoc$Construct)
r2 <- union(r2hoc, r2loc)
datatable(r2,
          filter = 'top',
          options = list(pageLength = nrow(r2)),
          rownames = FALSE,
          colnames = c('R²' = 2,
                        'R²adj' = 3),
          caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.249,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```
R² is below 0.25 for the Threat Beliefs lower-order constructs, but not below 0.1.
All other R² values are above 0.25, indicating weak in-sample predictive power at a minimum.
For Response Beliefs and Behavioral Intention, R² is above 0.5, indicating moderate in-sample predictive power.

# Effect size

Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
smhoc <- data.frame(model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target)
hocf2vec <- c()
for (i in 1:nrow(smhoc)){
  x = smhoc[i,1]
  y = smhoc[i, 2]
hocf2vec <- append(hocf2vec, summo$fSquare[[{{x}},{{y}}]])  
}
hocf2 <- smhoc %>% cbind(hocf2vec) %>% rename('f^2' = 3)
smloc <- data.frame(model$first_stage_model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target) %>%
  filter('Exogenous Construct' %notin% smhoc$`Exogenous Construct`)
locf2vec <- c()
for (i in 1:nrow(smloc)){
  x = smloc[i,1]
  y = smloc[i, 2]
locf2vec <- append(locf2vec, sumfs$fSquare[[{{x}},{{y}}]])  
}
locf2 <- smloc %>% cbind(locf2vec) %>% rename('f^2' = 3) %>% 
  filter(!(`Exogenous Construct` %in% hocf2$`Exogenous Construct` & `Endogenous Construct` %in% hocf2$`Endogenous Construct`))
f2 <- union(hocf2, locf2)
datatable(f2,
          filter = 'top',
          options = list(pageLength = nrow(f2)),
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00')))
```

The effect sizes of the relationships including many lower-order constructs are below 0.2.
Benevolence has only an effect on Perceived Response Costs and Perceived Severity.
Competence has an effect on all its descendant lower-order constructs except Perceived Susceptibility.
Integrity only has an effect on any of Perceived Response Efficacy.
Knowledge has a discernible effect only on Perceived Response Efficacy, Threat Beliefs and Perceived Severity.
From the lower-order constructs, only Perceived Response Efficacy and Perceived Response Costs have a discernible effect on Behavioral Intention.
Apart from that, there is only a negligible effect of Threat Beliefs on Behavioral Intention.
If this is mirrored in non-significant and irrelevant path coefficients, these structural relationships can be removed.
Other than that, all effects are small at a minimum.
The effects of Perceived Response Efficacy and Response Beliefs on Behavioral Intention are medium.
The effect of Distrusting Beliefs on both Threat Beliefs and Response Beliefs is large.

# Out-of-sample predictive performance

Out-of-sample predictive performance has to be evaluated using a simplified model without HOCs as an approximation as seminr as of now does not support plspredict for HOC.
If the root mean square error (RMSE) or the mean absolute deviation (MAD) of the naive LM model is below the ones for the PLS model, this indicates a lack of predictive performance.
However, a lack of predictive performance does not imply a lack of explanatory power.

```{r plspredict, echo = FALSE, layout="l-page"}
plspre <- predict_pls(proxymodel, noFolds = 10)
sumplspre <- summary(plspre)
oospp <- (as.data.frame(sumplspre$PLS_out_of_sample) %>%
  rbind(as.data.frame(sumplspre$LM_out_of_sample)) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[1,] - (as.data.frame(sumplspre$PLS_out_of_sample))[1,]) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[2,] - (as.data.frame(sumplspre$PLS_out_of_sample))[2,])  %>%
  cbind(`Prediction Errors` = c("PLS RMSE", "PLS MAD", "LM RMSE", "LM MAD", "RMSE Difference", "MAD Difference")))[c(1,3,5,2,4,6),c(ncol(sumplspre$PLS_out_of_sample)+1,1:ncol(sumplspre$PLS_out_of_sample))]
datatable(oospp,
          options = list(pageLength = nrow(oospp)),
          rownames = FALSE,
          caption = 'Out-of-sample predictive performance') %>%
  formatRound(-1,
              digits = 3) %>%
  formatStyle(names(oospp), backgroundColor = styleInterval(cuts = c(0), values = c('#ff9999', '#00')))
```

Only COTB1, COTB3 and COBI3 are predicted better by the model than the LM in terms of both RMSE and MAD.

# Significance and relevance of path coefficients

Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.

```{r path-coeff, echo = FALSE, layout="l-page"}
pcbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pcbasesplit <- base::strsplit(pcbase$Construct.Rel., "  ->  ")
pcbasesplit1 <- c()
pcbasesplit2 <- c()
for (i in 1:length(pcbasesplit)){
  pcbasesplit1 <- append(pcbasesplit1, pcbasesplit[[i]][1])
  pcbasesplit2 <- append(pcbasesplit2, pcbasesplit[[i]][2])
}
pclocbase <- rownames_to_column(as.data.frame(sumbofsmo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pclocbasesplit <- base::strsplit(pclocbase$Construct.Rel., "  ->  ")
pclocbasesplit1 <- c()
pclocbasesplit2 <- c()
for (i in 1:length(pclocbasesplit)){
  pclocbasesplit1 <- append(pclocbasesplit1, pclocbasesplit[[i]][1])
  pclocbasesplit2 <- append(pclocbasesplit2, pclocbasesplit[[i]][2])
}
pcdf <- (pcbase %>% 
  mutate('Exogenous Construct' = pcbasesplit1, 
         'Endogenous Construct' = pcbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pcbase$`T Stat.`),
         p = pt(abs(pcbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pcbase$`2.5% CI` < 0 &  pcbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pcdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- (pclocbase %>% 
  mutate('Exogenous Construct' = pclocbasesplit1, 
         'Endogenous Construct' = pclocbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pclocbase$`T Stat.`),
         p = pt(abs(pclocbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pclocbase$`2.5% CI` < 0 &  pclocbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pclocdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- pclocdf %>% filter(!(`Exogenous Construct` %in% pcdf$`Exogenous Construct` & `Endogenous Construct` %in% pcdf$`Endogenous Construct`))
pcalldf <- union(pcdf, pclocdf)
datatable(pcalldf,
          filter = 'top',
          options = list(pageLength = nrow(pcalldf)),
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcalldf)[9], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```

Concerning higher-order and regular constructs, only the path from Threat Beliefs to Behavioral Intention is non-significant.
With lower-order constructs, non-significant paths are those from Knowledge to Perceived Response Costs and Perceived Self-Efficacy, all from Benevolence except those from Perceived Response Costs and Perceived Severity, the path from Competence to Perceived Susceptibility,  all from Integrity except to Perceived Response Efficacy, all from the Threat Beliefs lower-order constructs and the one from Perceived Self-Efficacy,and both the paths from Descriptive and from Injunctive Norm to Behavioral Intention.

# Summary table

```{r summary table-df, echo = FALSE, include = FALSE}
sumsm <- pcdf[,-c(3,5:7)] %>% 
  left_join(hocf2)  %>%
  left_join(vif %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                           'Endogenous Construct' = 'Endogenous.Construct')) %>%
  rename('Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
         '0 in Path Coefficient CI' = '0 in CI',
         'Path Coefficient p' = 'p')
colnames(sumsm)[5] <- paste0("Path Coefficient t(", nrow(model$data), ")")
```
```{r summary table-df print, echo = FALSE, layout="l-page"}
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          colnames = c("f²" = 7),
          caption = 'Structural Model Summary') %>%
  formatRound(c(3,5:8),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[5], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00'))) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

# Results summary
Concerning higher-order and regular constructs, the path from Threat Beliefs to Behavioral Intention is non-significant and the effect size is negligible.
Therefore the path and the Threat Beliefs construct can be removed.
All other paths are significant and the effects, with the exception of the effect of Knowledge on Response Beliefs, are at least weak.
Concerning the remaining lower-order constructs, Benevolence only has a significant path with a discernible effect to Perceived Response Costs, and Integrity only to Perceived Response Efficacy.
Knowledge only has a significant path with a discernible effect to Perceived Response Efficacy.
Perceived Self-Efficacy has no significant path to or discernible effect on Behavioral Intention.
Therefore, Perceived Self-Efficacy could be removed as a lower-order construct.
Neither Descriptive nor Injunctive Norm have  a significant path to or a discernible effect on Behavioral Intention, though Subjective Norm has both.
As Injunctive Norm is the comparatively weaker construct, it should be removed for the next model iteration and Descriptive Norm should replace the Subjective Norm HOC to assess wether it has a significant effect on its own.
To differentiate the influence of Distrusting Beliefs and Knowledge on the Response Beliefs lower-order construct, an alternative model with the Response Beliefs lower-order constructs split up should be estimated.
