---
title: "COVID-19 Model Iteration 2 Nonlinearity Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
# Load models and create summaries
# Load PLS Model
model <- readRDS("Models/model-co-2.RDS")
bootmodel <- readRDS("Models/model-boot-co-2.RDS")
# Load bootstrapped first stage PLS model
bootfsmodel <- readRDS("Models/model-fs-boot-co-2.RDS")
# Load approximation PLS model (no HOCs, data formatted as data.frame)
proxymodel <- readRDS("Models/model-proxy-co-2.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
sumprmo <- summary(proxymodel)
# Bootstrap proxy model (500 samples) for comparability
bootprmodel <- bootstrap_model(proxymodel)
sumboprmo <- summary(bootprmodel)
# Set seminr plot theme
thm <- seminr_theme_create(construct.compositeA.arrow = "backward", construct.compositeA.use_weights = FALSE, plot.adj = FALSE)
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Nonlinearity
If any of the test statistics is significant, the respective partial regression might be nonlinear.
```{r reset}
# Estimate partial linear models + proxy models for HOCs
lmbi1 <- lm(model$construct_scores[,"Behavioral Intention"] ~ model$construct_scores[,c("Response Beliefs")])
lmbi1prox  <- lm(proxymodel$construct_scores[,"Behavioral Intention"] ~ proxymodel$construct_scores[,c("Response Beliefs")])
lmbi2 <- lm(model$construct_scores[,"Behavioral Intention"] ~ model$construct_scores[,c("Threat Beliefs")])
lmbi2prox <- lm(proxymodel$construct_scores[,"Behavioral Intention"] ~ proxymodel$construct_scores[,c("Threat Beliefs")])
lmbi3 <- lm(model$construct_scores[,"Behavioral Intention"] ~ model$construct_scores[,c("Personal Moral Norm")])
lmbi4 <- lm(model$construct_scores[,"Behavioral Intention"] ~ model$construct_scores[,c("Subjective Norm")])
lmbi4prox <- lm(proxymodel$construct_scores[,"Behavioral Intention"] ~ proxymodel$construct_scores[,c("Subjective Norm")])
lmrb1 <- lm(model$construct_scores[,"Response Beliefs"] ~ model$construct_scores[,c("Distrusting Beliefs")])
lmrb1prox <- lm(proxymodel$construct_scores[,"Response Beliefs"] ~ proxymodel$construct_scores[,c("Distrusting Beliefs")])
lmrb2 <- lm(model$construct_scores[,"Response Beliefs"] ~ model$construct_scores[,c("Knowledge")])
lmtb1 <- lm(model$construct_scores[,"Threat Beliefs"] ~ model$construct_scores[,c("Distrusting Beliefs")])
lmtb1prox <- lm(proxymodel$construct_scores[,"Threat Beliefs"] ~ proxymodel$construct_scores[,c("Distrusting Beliefs")])
lmtb2 <- lm(model$construct_scores[,"Threat Beliefs"] ~ model$construct_scores[,c("Knowledge")])
# Apply reset test
resettest(lmbi1)
resettest(lmbi1prox)
resettest(lmbi2)
resettest(lmbi2prox)
resettest(lmbi3)
resettest(lmbi4)
resettest(lmbi4prox)
resettest(lmrb1)
resettest(lmrb1prox)
resettest(lmrb2)
resettest(lmtb1)
resettest(lmtb1prox)
resettest(lmtb2)
```
Using p = 0.05 as a threshold, there are potential nonlinear effects in the partial regression equations for the influence of Response Beliefs (original: p < 0.001, proxy: p = 0.011), Threat Beliefs (original and proxy: p < 0.001), and Subjective Norm (original: p = 0.012, proxy: p = 0.018) on Behavioral Intention.
The same is potentially true for the effects of Distrusting Beliefs (original: p = 0.021, proxy: p = 0.124) and Knowledge (p = 0.006) on Response Beliefs, an for the effects of Distrusting Beliefs (orginal: p < 0.001, proxy: p = 0.003) and Knowledge (p = 0.022) on Threat Beliefs.

## Test alternate nonlinear effects
To test for nonlinearity, one can model an interaction term of the exogenous construct with itself.

### Response Beliefs on Behavioral Intention
```{r bi1 alt nonlinear estimate}
# Estimate alternate model with quadratic effect - HOCs as proxy
mobi1alt <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Response Beliefs 1", multi_items("CORB", c(4:10)), weights = mode_B),
    composite("Response Beliefs 2", multi_items("CORB", c(4:10)), weights = mode_B),
    interaction_term("Response Beliefs 1", "Response Beliefs 2", method = two_stage),
    composite("Benevolence", multi_items("CODI", 1:3)),
    composite("Competence", multi_items("CODI", 4:6)),
    composite("Integrity", multi_items("CODI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Knowledge", single_item("COKN")),
    composite("Perceived Susceptibility", multi_items("COTB", 1:3)),
    composite("Perceived Severity", multi_items("COTB", 4:6)),
    higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B),
    composite("Personal Moral Norm", multi_items("COPN", c(1,3))),
    composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B)
  ),
  structural_model = relationships(
    paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs 1", "Response Beliefs 2", "Threat Beliefs")),
    paths(from = c("Response Beliefs 1*Response Beliefs 2", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
# Estimate second model for f2 with construct excluded
mobi1altex <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Benevolence", multi_items("CODI", 1:3)),
    composite("Competence", multi_items("CODI", 4:6)),
    composite("Integrity", multi_items("CODI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Knowledge", single_item("COKN")),
    composite("Perceived Susceptibility", multi_items("COTB", 1:3)),
    composite("Perceived Severity", multi_items("COTB", 4:6)),
    higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B),
    composite("Personal Moral Norm", multi_items("COPN", c(1,3))),
    composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B)
  ),
  structural_model = relationships(
    paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Threat Beliefs")),
    paths(from = c("Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
# Bootstrap model for significance (500 samples)
bomobi1alt <- bootstrap_model(mobi1alt)
sumbomobi1alt <- summary(bomobi1alt)
```
```{r bi1 alt nonlinear assess}
# Assess impact using f² and significance
bi1compdf <- data.frame(
  Model = c("Original Model", "Proxy Model", "Quadratic Model"), 
  `f²` = c(
    summo$fSquare["Response Beliefs", "Behavioral Intention"],
    sumprmo$fSquare["Response Beliefs", "Behavioral Intention"],
    (mobi1alt$rSquared[1,"Behavioral Intention"]-mobi1altex$rSquared[1,"Behavioral Intention"])/(1-mobi1alt$rSquared[1,"Behavioral Intention"])
  ),
  `t-value` = c(sumbomo$bootstrapped_paths[5,4], sumboprmo$bootstrapped_paths[5,4], sumbomobi1alt$bootstrapped_paths[7,4])
)
bi1compdf 
```
For the alternate model with Response Beliefs as a quadratic influence, the effect size is smaller, as well as the t-value.
This points to a linear effect of Response Beliefs on Behavioral Intention.

### Threat Beliefs on Behavioral Intention
```{r bi2 alt nonlinear estimate}
# Estimate alternate model with quadratic effect - HOCs as proxy
mobi2alt <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Perceived Self-Efficacy", single_item("CORB10")),
    composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B),
    composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B),
    higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B),
    composite("Benevolence", multi_items("CODI", 1:3)),
    composite("Competence", multi_items("CODI", 4:6)),
    composite("Integrity", multi_items("CODI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Knowledge", single_item("COKN")),
    composite("Threat Beliefs 1", multi_items("COTB", 1:6), weights = mode_B),
    composite("Threat Beliefs 2", multi_items("COTB", 1:6), weights = mode_B),
    interaction_term("Threat Beliefs 1", "Threat Beliefs 2", method = two_stage),
    composite("Personal Moral Norm", multi_items("COPN", c(1,3))),
    composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B)
  ),
  structural_model = relationships(
    paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs", "Threat Beliefs 1", "Threat Beliefs 2")),
    paths(from = c("Response Beliefs", "Threat Beliefs 1*Threat Beliefs 2", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
# Estimate second model for f2 with construct excluded
mobi2altex <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Perceived Self-Efficacy", single_item("CORB10")),
    composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B),
    composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B),
    higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B),
    composite("Benevolence", multi_items("CODI", 1:3)),
    composite("Competence", multi_items("CODI", 4:6)),
    composite("Integrity", multi_items("CODI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Knowledge", single_item("COKN")),
    composite("Personal Moral Norm", multi_items("COPN", c(1,3))),
    composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B)
  ),
  structural_model = relationships(
    paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs")),
    paths(from = c("Response Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
# Bootstrap model for significance (500 samples)
bomobi2alt <- bootstrap_model(mobi2alt)
sumbomobi2alt <- summary(bomobi2alt)
```
```{r bi2 alt nonlinear assess}
# Assess impact using f² and significance
bi2compdf <- data.frame(
  Model = c("Original Model", "Proxy Model", "Quadratic Model"), 
  `f²` = c(
    summo$fSquare["Threat Beliefs", "Behavioral Intention"],
    sumprmo$fSquare["Threat Beliefs", "Behavioral Intention"],
    (mobi2alt$rSquared[1,"Behavioral Intention"]-mobi2altex$rSquared[1,"Behavioral Intention"])/(1-mobi2alt$rSquared[1,"Behavioral Intention"])
  ),
  `t-value` = c(sumbomo$bootstrapped_paths[6,4], sumboprmo$bootstrapped_paths[6,4], sumbomobi2alt$bootstrapped_paths[8,4])
)
bi2compdf 
```
For the alternate model with Threat Beliefs as a quadratic influence, the effect size is smaller, as is the t-value.
This points to a linear effect of Threat Beliefs on Behavioral Intention.

<!-- ### Subjective Norm on Behavioral Intention -->
<!-- ```{r bi3 alt nonlinear estimate} -->
<!-- # Estimate alternate model with quadratic effect - HOCs as proxy -->
<!-- mobi3altmm <- constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Benevolence", multi_items("CODI", 1:3)), -->
<!--     composite("Competence", multi_items("CODI", 4:6)), -->
<!--     composite("Integrity", multi_items("CODI", 7:9)), -->
<!--     higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Perceived Susceptibility", multi_items("COTB", 1:3)), -->
<!--     composite("Perceived Severity", multi_items("COTB", 4:6)), -->
<!--     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Subjective Norm 1", c("CCDN1", "CCDN2", "CCIN1", "CCIN2"), mode_B), -->
<!--     composite("Subjective Norm 2", c("CCDN1", "CCDN2", "CCIN1", "CCIN2"), mode_B), -->
<!--     interaction_term("Subjective Norm 1", "Subjective Norm 2", method = two_stage), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ) -->
<!-- mobi3altsm <- relationships( -->
<!--     paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs", "Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm 1*Subjective Norm 2"), to = "Behavioral Intention")) -->
<!-- mobi3alt <- estimate_pls(data = model$data, mobi3altmm, mobi3altsm) -->
<!-- # Estimate second model for f2 with construct excluded -->
<!-- mobi3altex <- estimate_pls( -->
<!--   data = model$data, -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Benevolence", multi_items("CODI", 1:3)), -->
<!--     composite("Competence", multi_items("CODI", 4:6)), -->
<!--     composite("Integrity", multi_items("CODI", 7:9)), -->
<!--     higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Subjective Norm 1", c(multi_items("CODN", 1:2), multi_items("COIN", 1:2)), mode_B), -->
<!--     composite("Subjective Norm 2", c(multi_items("CODN", 1:2), multi_items("COIN", 1:2)), mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs", "Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Personal Moral Norm", "Threat Beliefs"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Bootstrap model for significance (500 samples) -->
<!-- bomobi3alt <- bootstrap_model(mobi3alt) -->
<!-- sumbomobi3alt <- summary(bomobi3alt) -->
<!-- ``` -->
<!-- ```{r bi3 alt nonlinear assess} -->
<!-- # Assess impact using f² and significance -->
<!-- bi3compdf <- data.frame( -->
<!--   Model = c("Original Model", "Proxy Model", "Quadratic Model"), -->
<!--   `f²` = c( -->
<!--     summo$fSquare["Threat Beliefs", "Behavioral Intention"], -->
<!--     sumprmo$fSquare["Threat Beliefs", "Behavioral Intention"], -->
<!--     (mobi3alt$rSquared[1,"Behavioral Intention"]-mobi3altex$rSquared[1,"Behavioral Intention"])/(1-mobi3alt$rSquared[1,"Behavioral Intention"]) -->
<!--   ), -->
<!--   `t-value` = c(sumbomo$bootstrapped_paths[6,4], sumboprmo$bootstrapped_paths[6,4], sumbomobi3alt$bootstrapped_paths[8,4]) -->
<!-- ) -->
<!-- bi3compdf -->
<!-- ``` -->
The Subjective Norm alternative model cannot be assessed.

<!-- ## Distrusting Beliefs on Response Beliefs -->
<!-- ```{r rb1 alt nonlinear estimate} -->
<!-- # Estimate alternate model with quadratic effect - HOCs as proxy -->
<!-- morb1alt <- estimate_pls( -->
<!--   data = model$data, -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Distrusting Beliefs 1", multi_items("CODI", 1:9), weights = mode_B), -->
<!--     composite("Distrusting Beliefs 2", multi_items("CODI", 1:9), weights = mode_B), -->
<!--     interaction_term("Distrusting Beliefs 1", "Distrusting Beliefs 2", method = two_stage), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Perceived Susceptibility", multi_items("COTB", 1:3)), -->
<!--     composite("Perceived Severity", multi_items("COTB", 4:6)), -->
<!--     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!--     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Distrusting Beliefs 1*Distrusting Beliefs 2", "Knowledge"), to = c("Response Beliefs")), -->
<!--     paths(from = c("Distrusting Beliefs 1", "Knowledge"), to = c("Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Estimate second model for f2 with construct excluded -->
<!-- morb1altex <- estimate_pls( -->
<!--   data = model$data, -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Benevolence", multi_items("CODI", 1:3)), -->
<!--     composite("Competence", multi_items("CODI", 4:6)), -->
<!--     composite("Integrity", multi_items("CODI", 7:9)), -->
<!--     higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!--     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs", "Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Bootstrap model for significance (500 samples) -->
<!-- bomorb1alt <- bootstrap_model(morb1alt) -->
<!-- sumbomorb1alt <- summary(bomorb1alt) -->
<!-- ``` -->
<!-- ```{r rb1 alt nonlinear assess} -->
<!-- # Assess impact using f² and significance -->
<!-- rb1compdf <- data.frame( -->
<!--   Model = c("Original Model", "Proxy Model", "Quadratic Model"), -->
<!--   `f²` = c( -->
<!--     summo$fSquare["Threat Beliefs", "Behavioral Intention"], -->
<!--     sumprmo$fSquare["Threat Beliefs", "Behavioral Intention"], -->
<!--     (morb1alt$rSquared[1,"Behavioral Intention"]-morb1altex$rSquared[1,"Behavioral Intention"])/(1-morb1alt$rSquared[1,"Behavioral Intention"]) -->
<!--   ), -->
<!--   `t-value` = c(sumbomo$bootstrapped_paths[6,4], sumboprmo$bootstrapped_paths[6,4], sumbomorb1alt$bootstrapped_paths[8,4]) -->
<!-- ) -->
<!-- rb1compdf -->
<!-- ``` -->
The alternative model for a quadratic influence of Distrusting Beliefs on Response Beliefs cannot be estimated.

<!-- ## Knowledge Beliefs on Response Beliefs -->
<!-- ```{r rb2 alt nonlinear estimate} -->
<!-- # Estimate alternate model with quadratic effect - HOCs as proxy -->
<!-- morb2alt <- estimate_pls( -->
<!--   data = model$data, -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Benevolence", multi_items("CODI", 1:3)), -->
<!--     composite("Competence", multi_items("CODI", 4:6)), -->
<!--     composite("Integrity", multi_items("CODI", 7:9)), -->
<!--     higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!--     composite("Knowledge1", single_item("COKN")), -->
<!--     composite("Knowledge2", single_item("COKN")), -->
<!--     interaction_term("Knowledge1", "Knowledge2", method = product_indicator), -->
<!--     composite("Perceived Susceptibility", multi_items("COTB", 1:3)), -->
<!--     composite("Perceived Severity", multi_items("COTB", 4:6)), -->
<!--     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!--     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Distrusting Beliefs", "Knowledge1*Knowledge2"), to = c("Response Beliefs")), -->
<!--     paths(from = c("Distrusting Beliefs", "Knowledge1"), to = c("Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Estimate second model for f2 with construct excluded -->
<!-- morb1altex <- estimate_pls( -->
<!--   data = model$data, -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Benevolence", multi_items("CODI", 1:3)), -->
<!--     composite("Competence", multi_items("CODI", 4:6)), -->
<!--     composite("Integrity", multi_items("CODI", 7:9)), -->
<!--     higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!--     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Response Beliefs", "Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Bootstrap model for significance (500 samples) -->
<!-- bomorb1alt <- bootstrap_model(morb1alt) -->
<!-- sumbomorb1alt <- summary(bomorb1alt) -->
<!-- ``` -->
<!-- ```{r rb1 alt nonlinear assess} -->
<!-- # Assess impact using f² and significance -->
<!-- rb1compdf <- data.frame( -->
<!--   Model = c("Original Model", "Proxy Model", "Quadratic Model"), -->
<!--   `f²` = c( -->
<!--     summo$fSquare["Threat Beliefs", "Behavioral Intention"], -->
<!--     sumprmo$fSquare["Threat Beliefs", "Behavioral Intention"], -->
<!--     (morb1alt$rSquared[1,"Behavioral Intention"]-morb1altex$rSquared[1,"Behavioral Intention"])/(1-morb1alt$rSquared[1,"Behavioral Intention"]) -->
<!--   ), -->
<!--   `t-value` = c(sumbomo$bootstrapped_paths[6,4], sumboprmo$bootstrapped_paths[6,4], sumbomorb1alt$bootstrapped_paths[8,4]) -->
<!-- ) -->
<!-- rb1compdf -->
<!-- ``` -->
The alternative model for a quadratic effect of Knowledge on Threat Beliefs cannot be estimated.
