---
title: "COVID-19 Model Iteration 3-b-2 Endogeneity Evaluation"
output: html_document
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(nortest)
library(car)
# Load models and create summaries
# Load PLS Model
model <- readRDS("Models/model-co-3-b-2.RDS")
bootmodel <- readRDS("Models/model-boot-co-3-b-2.RDS")
# Load bootstrapped first stage PLS model
bootfsmodel <- readRDS("Models/model-fs-boot-co-3-b-2.RDS")
# Load approximation PLS model (no HOCs, data formatted as data.frame)
proxymodel <- readRDS("Models/model-proxy-co-3-b-2.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
sumprmo <- summary(proxymodel)
# # Bootstrap proxy model (500 samples) for comparability
# bootprmodel <- bootstrap_model(proxymodel)
# sumboprmo <- summary(bootprmodel)
# Function for Gaussian Capula Approach
createCopula <- function(P){
	H.p <- stats::ecdf(P)
	H.p <- H.p(P)
	H.p <- ifelse(H.p==0,0.0000001,H.p)
	H.p <- ifelse(H.p==1,0.9999999,H.p)
	U.p <- H.p
	p.star <- stats::qnorm(U.p)
	return(p.star)	
}
bootstrappedSignificance <- function(dataset, bootstrapresults, numIndependentVariables, numCopulas){
	for (i in 1:nrow(summary(bootstrapresults))){
		t <- summary(bootstrapresults)[i, "original"] / summary(bootstrapresults)[i, "bootSE"]
		# df = n (number of observations) - k (number of independent variables + copulas) - 1
		pvalue <- 2 * pt(-abs(t),df=nrow(dataset)-numIndependentVariables-numCopulas-1)
		cat("Pr(>|t|)", rownames(summary(bootstrapresults))[i], ": ", pvalue, "\n")
	}
}
bootSig <- function(dataset, bootstrapresults, numIndependentVariables, numCopulas){
  bootSigvec <- vector("double", length = length(numIndependentVariables + 1))
	for (i in 1:nrow(summary(bootstrapresults))){
	  t <- summary(bootstrapresults)[i, "original"] / summary(bootstrapresults)[i, "bootSE"]
		# df = n (number of observations) - k (number of independent variables + copulas) - 1
		bootSigvec[i] <- 2 * pt(-abs(t),df=nrow(dataset)-numIndependentVariables-numCopulas-1)
	}
  return(bootSigvec)
}
```
The code for the assessment of endogeneity using the Gaussian Copula approach comes from

Hult, G. T. M., J. F. Hair, D. Proksch, M. Sarstedt, A. Pinkwart, & C. M. Ringle (2018).
Addressing Endogeneity in International Marketing Applications of Partial Least Squares Structural Equation Modeling. Journal of International Marketing, 26(3), 1–21. https://doi.org/10.1509/jim.17.0151


# Test of non-normality
The Gaussian Copula approach can only be used if the independent variable in question is non-normally distributed.
```{r}
# Find out if independent (i.e., exogenous) variables are non-normally distributed
# If yes, Gaussian Copula approach can be used.
#Distrusting Beliefs
shapiro.test(model$construct_scores[,"Distrusting Beliefs"])
lillie.test(model$construct_scores[,"Distrusting Beliefs"])
ggplot(as.data.frame(model$construct_scores), aes(`Distrusting Beliefs`)) +
  geom_density()
# Knowledge
shapiro.test(model$construct_scores[,"Knowledge"])
lillie.test(model$construct_scores[,"Knowledge"])
ggplot(as.data.frame(model$construct_scores), aes(`Knowledge`)) +
  geom_density()
# Perceived Response Efficacy
shapiro.test(model$construct_scores[,"Perceived Response Efficacy"])
lillie.test(model$construct_scores[,"Perceived Response Efficacy"])
ggplot(as.data.frame(model$construct_scores), aes(`Perceived Response Efficacy`)) +
  geom_density()
# Perceived Response Costs
shapiro.test(model$construct_scores[,"Perceived Response Costs"])
lillie.test(model$construct_scores[,"Perceived Response Costs"])
ggplot(as.data.frame(model$construct_scores), aes(`Perceived Response Costs`)) +
  geom_density()
# Personal Moral Norm
shapiro.test(model$construct_scores[,"Personal Moral Norm"])
lillie.test(model$construct_scores[,"Personal Moral Norm"])
ggplot(as.data.frame(model$construct_scores), aes(`Personal Moral Norm`)) +
  geom_density()
# Descriptive Norm
shapiro.test(model$construct_scores[,"Descriptive Norm"])
lillie.test(model$construct_scores[,"Descriptive Norm"])
ggplot(as.data.frame(model$construct_scores), aes(`Descriptive Norm`)) +
  geom_density()
```
All independent (or endogenous) variables are non-normally distributed.
Therefore, the Gaussian Copula approach can be used for all of them.


# Regression of Perceived Response Efficacy Beliefs on Distrusting Beliefs and Knowledge
```{r gca pre}
# Define Variables for easy access
KN <- model$construct_scores[,"Knowledge"]
DI <- model$construct_scores[,"Distrusting Beliefs"]
PRE <- model$construct_scores[,"Perceived Response Efficacy"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
premodel <- lm(PRE ~ DI + KN)
summary(premodel)
bootpre <- Boot(premodel, R=bootrounds)
summary(bootpre)

# Make base df
predf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootpre)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootpre, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables
KN_star <- createCopula(KN)
DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladipre <- lm(PRE ~ DI + KN + DI_star + 0)
summary(copuladipre)
# Bootstrap Standard Errors
bootcopuladipre <- Boot(copuladipre, R=bootrounds)
summary(bootcopuladipre)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladipre, 2,1)
# Attach to df
predf <- predf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladipre)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladipre, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulaknpre <- lm(PRE ~ DI + KN + KN_star + 0)
summary(copulaknpre)
# Bootstrap Standard Errors
bootcopulaknpre <- Boot(copulaknpre, R=bootrounds)
summary(bootcopulaknpre)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaknpre, 2,1)
# Attach to df
predf <- predf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulaknpre)[1:2,5], NA, summary(bootcopulaknpre)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopulaknpre, 2,1)[1:2], NA, bootSig(model$data, bootcopulaknpre, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladiknpre <- lm(PRE ~ DI + KN + DI_star + KN_star + 0)
summary(copuladiknpre)
# Bootstrap Standard Errors
bootcopuladiknpre <- Boot(copuladiknpre, R=bootrounds)
summary(bootcopuladiknpre)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladiknpre, 2, 2)
# Attach to df
predf <- predf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladiknpre)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladiknpre, 2, 2))
)
datatable(predf) %>%
  formatRound(-1,
              digits = 3)
```
Neither the Distrusting Beliefs nor the Knowledge Copula is significant, indicating that there is no hidden endogeneity in the regression of Perceived Response Efficacy on its predictors.

# Regression of Perceived Response Costs Beliefs on Distrusting Beliefs and Knowledge
```{r gca prc}
# Define Variables for easy access
KN <- model$construct_scores[,"Knowledge"]
DI <- model$construct_scores[,"Distrusting Beliefs"]
PRC <- model$construct_scores[,"Perceived Response Costs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
prcmodel <- lm(PRC ~ DI + KN)
summary(prcmodel)
bootprc <- Boot(prcmodel, R=bootrounds)
summary(bootprc)

# Make base df
prcdf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootprc)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootprc, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables
KN_star <- createCopula(KN)
DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladiprc <- lm(PRC ~ DI + KN + DI_star + 0)
summary(copuladiprc)
# Bootstrap Standard Errors
bootcopuladiprc <- Boot(copuladiprc, R=bootrounds)
summary(bootcopuladiprc)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladiprc, 2,1)
# Attach to df
prcdf <- prcdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladiprc)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladiprc, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulaknprc <- lm(PRC ~ DI + KN + KN_star + 0)
summary(copulaknprc)
# Bootstrap Standard Errors
bootcopulaknprc <- Boot(copulaknprc, R=bootrounds)
summary(bootcopulaknprc)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaknprc, 2,1)
# Attach to df
prcdf <- prcdf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulaknprc)[1:2,5], NA, summary(bootcopulaknprc)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopulaknprc, 2,1)[1:2], NA, bootSig(model$data, bootcopulaknprc, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladiknprc <- lm(PRC ~ DI + KN + DI_star + KN_star + 0)
summary(copuladiknprc)
# Bootstrap Standard Errors
bootcopuladiknprc <- Boot(copuladiknprc, R=bootrounds)
summary(bootcopuladiknprc)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladiknprc, 2, 2)
# Attach to df
prcdf <- prcdf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladiknprc)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladiknprc, 2, 2))
)
datatable(prcdf) %>%
  formatRound(-1,
              digits = 3)
```
Neither the Distrusting Beliefs nor the Knowledge Copula is significant, indicating that there is no hidden endogeneity in the regression of Perceived Response Costs on its predictors.

# Regression of Behavioral Intention on its predictors
```{r gca bi}
# Define Variables for easy access
BI <- model$construct_scores[,"Behavioral Intention"]
PN <- model$construct_scores[,"Personal Moral Norm"]
DN <- model$construct_scores[,"Descriptive Norm"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
bimodel <- lm(BI ~ PRE + PRC  + PN + DN)
summary(bimodel)
bootbi <- Boot(bimodel, R=bootrounds)
summary(bootbi)

# Make base df
bidf <- data.frame(Construct = c("Perceived Response Efficacy", "Perceived Response Costs", "Personal Moral Norm", "Descriptive Norm", "Copula Perceived Response Efficacy", "Copula Perceived Response Costs", "Copula Personal Moral Norm", "Copula Descriptive Norm"), 
                   Original.Model.Value = c(summary(bootbi)[2:5,5],NA,NA,NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootbi, 3, 0)[2:5],NA,NA,NA,NA)
)

# Calculate copulas for independent variables - already happened
PRE_star <- createCopula(PRE)
PRC_star <- createCopula(PRC)
PN_star <- createCopula(PN)
DN_star <- createCopula(DN)

# Calculate results with copula for Perceived Response Efficacy
# Input is regular model + copula + 0
copulaprebi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + 0)
summary(copulaprebi)
# Bootstrap Standard Errors
bootcopulaprebi <- Boot(copulaprebi)
summary(bootcopulaprebi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprebi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.Co.Model.Value = c(summary(bootcopulaprebi)[,5], NA, NA, NA),
  PRE.Co.Model.p = c(bootSig(model$data, bootcopulaprebi, 4,1), NA, NA, NA)
)

# Calculate results with copula for Perceived Response Costs
# Input is regular model + copula + 0
copulaprcbi <- lm(BI ~ PRE + PRC + PN + DN + PRC_star + 0)
summary(copulaprcbi)
# Bootstrap Standard Errors
bootcopulaprcbi <- Boot(copulaprcbi)
summary(bootcopulaprcbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprcbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  PRC.Co.Model.Value = c(summary(bootcopulaprcbi)[1:4,5], NA, summary(bootcopulaprcbi)[5,5],  NA, NA),
  PRC.Co.Model.p = c(bootSig(model$data, bootcopulaprcbi, 4,1)[1:4], NA, bootSig(model$data, bootcopulaprcbi, 4,1)[5], NA, NA)
)

# Calculate results with copula for Personal Moral Norm
# Input is regular model + copula + 0
copulapnbi <- lm(BI ~ PRE + PRC + PN + DN + PN_star + 0)
summary(copulapnbi)
# Bootstrap Standard Errors
bootcopulapnbi <- Boot(copulapnbi)
summary(bootcopulapnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapnbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  PN.Co.Model.Value = c(summary(bootcopulapnbi)[1:4,5], NA, NA, summary(bootcopulapnbi)[5,5],  NA),
  PN.Co.Model.p = c(bootSig(model$data, bootcopulapnbi, 4,1)[1:4], NA, NA, bootSig(model$data, bootcopulapnbi, 4,1)[5],NA)
)

# Calculate results with copula for Descriptive Norm
# Input is regular model + copula + 0
copuladnbi <- lm(BI ~ PRE + PRC + PN + DN + PN_star + 0)
summary(copuladnbi)
# Bootstrap Standard Errors
bootcopuladnbi <- Boot(copuladnbi)
summary(bootcopuladnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladnbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  DN.Co.Model.Value = c(summary(bootcopuladnbi)[1:4,5], NA, NA, NA, summary(bootcopuladnbi)[5,5]),
  DN.Co.Model.p = c(bootSig(model$data, bootcopuladnbi, 4,1)[1:4], NA, NA, NA, bootSig(model$data, bootcopuladnbi, 4,1)[5])
)

# Calculate results with copula for Perceived Response Efficacy and Perceived Response Costs
# Input is regular model + copula + 0
copulapreprcbi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + PRC_star + 0)
summary(copulapreprcbi)
# Bootstrap Standard Errors
bootcopulapreprcbi <- Boot(copulapreprcbi)
summary(bootcopulapreprcbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapreprcbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.PRC.Co.Model.Value = c(summary(bootcopulapreprcbi)[,5], NA, NA),
  PRE.PRC.Co.Model.p = c(bootSig(model$data, bootcopulapreprcbi, 4,2), NA, NA)
)

# Calculate results with copula for Perceived Response Efficacy and Personal Moral Norm
# Input is regular model + copula + 0
copulaprepnbi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + PN_star + 0)
summary(copulaprepnbi)
# Bootstrap Standard Errors
bootcopulaprepnbi <- Boot(copulaprepnbi)
summary(bootcopulaprepnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprepnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.PN.Co.Model.Value = c(summary(bootcopulaprepnbi)[1:5,5], NA, summary(bootcopulaprepnbi)[6,5], NA),
  PRE.PN.Co.Model.p = c(bootSig(model$data, bootcopulaprepnbi, 4,2)[1:5], NA, bootSig(model$data, bootcopulaprepnbi, 4,2)[6], NA)
)

# Calculate results with copula for Perceived Response Efficacy and Descriptive Norm
# Input is regular model + copula + 0
copulaprednbi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + DN_star + 0)
summary(copulaprednbi)
# Bootstrap Standard Errors
bootcopulaprednbi <- Boot(copulaprednbi)
summary(bootcopulaprednbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprednbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.DN.Co.Model.Value = c(summary(bootcopulaprednbi)[1:5,5], NA, NA, summary(bootcopulaprednbi)[6,5]),
  PRE.DN.Co.Model.p = c(bootSig(model$data, bootcopulaprednbi, 4,2)[1:5], NA, NA, bootSig(model$data, bootcopulaprednbi, 4,2)[6])
)

# Calculate results with copula for Perceived Response Costs and Personal Moral Norm
# Input is regular model + copula + 0
copulaprcpnbi <- lm(BI ~ PRE + PRC + PN + DN + PRC_star + PN_star + 0)
summary(copulaprcpnbi)
# Bootstrap Standard Errors
bootcopulaprcpnbi <- Boot(copulaprcpnbi)
summary(bootcopulaprcpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprcpnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PRC.PN.Co.Model.Value = c(summary(bootcopulaprcpnbi)[1:4,5], NA, summary(bootcopulaprcpnbi)[5:6,5], NA),
  PRC.PN.Co.Model.p = c(bootSig(model$data, bootcopulaprcpnbi, 4,2)[1:4], NA, bootSig(model$data, bootcopulaprcpnbi, 4,2)[5:6], NA)
)

# Calculate results with copula for Perceived Response Costs and Descriptive Norm
# Input is regular model + copula + 0
copulaprcdnbi <- lm(BI ~ PRE + PRC + PN + DN + PRC_star + DN_star + 0)
summary(copulaprcdnbi)
# Bootstrap Standard Errors
bootcopulaprcdnbi <- Boot(copulaprcdnbi)
summary(bootcopulaprcdnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprcdnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PRC.DN.Co.Model.Value = c(summary(bootcopulaprcdnbi)[1:4,5], NA, summary(bootcopulaprcdnbi)[5,5], NA, summary(bootcopulaprcdnbi)[6,5]),
  PRC.DN.Co.Model.p = c(bootSig(model$data, bootcopulaprcdnbi, 4,2)[1:4], NA, bootSig(model$data, bootcopulaprcdnbi, 4,2)[5], NA, bootSig(model$data, bootcopulaprcdnbi, 4,2)[6])
)


# Calculate results with copula for Personal Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copulapndnbi <- lm(BI ~ PRE + PRC + PN + DN + PN_star + DN_star + 0)
summary(copulapndnbi)
# Bootstrap Standard Errors
bootcopulapndnbi <- Boot(copulapndnbi)
summary(bootcopulapndnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapndnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PN.DN.Co.Model.Value = c(summary(bootcopulapndnbi)[1:4,5], NA, NA, summary(bootcopulapndnbi)[5:6,5]),
  PN.DN.Co.Model.p = c(bootSig(model$data, bootcopulapndnbi, 4,2)[1:4], NA, NA, bootSig(model$data, bootcopulapndnbi, 4,2)[5:6])
)

# Calculate results with copula for Perceived Response Efficacy, Perceived Response Costs and Perceived Moral Norm
# Input is regular model + copula + 0
copulapreprcpnbi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + PRC_star + PN_star + 0)
summary(copulapreprcpnbi)
# Bootstrap Standard Errors
bootcopulapreprcpnbi <- Boot(copulapreprcpnbi)
summary(bootcopulapreprcpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapreprcpnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.PRC.PN.Co.Model.Value = c(summary(bootcopulapreprcpnbi)[,5], NA),
  PRE.PRC.PN.Co.Model.p = c(bootSig(model$data, bootcopulapreprcpnbi, 4,3), NA)
)

# Calculate results with copula for Perceived Response Efficacy, Perceived Response Costs and Descriptive Norm
# Input is regular model + copula + 0
copulapreprcdnbi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + PRC_star + DN_star + 0)
summary(copulapreprcdnbi)
# Bootstrap Standard Errors
bootcopulapreprcdnbi <- Boot(copulapreprcdnbi)
summary(bootcopulapreprcdnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapreprcdnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.PRC.DN.Co.Model.Value = c(summary(bootcopulapreprcdnbi)[1:6,5], NA, summary(bootcopulapreprcdnbi)[7,5]),
  PRE.PRC.DN.Co.Model.p = c(bootSig(model$data, bootcopulapreprcdnbi, 4,3)[1:6], NA, bootSig(model$data, bootcopulapreprcdnbi, 4,3)[7])
)


# Calculate results with copula for Perceived Response Costs, Personal Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copulaprcpndnbi <- lm(BI ~ PRE + PRC + PN + DN + PRC_star + PN_star + DN_star + 0)
summary(copulaprcpndnbi)
# Bootstrap Standard Errors
bootcopulaprcpndnbi <- Boot(copulaprcpndnbi)
summary(bootcopulaprcpndnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaprcpndnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.PRC.DN.Co.Model.Value = c(summary(bootcopulaprcpndnbi)[1:4,5], NA, summary(bootcopulaprcpndnbi)[5:7,5]),
  PRE.PRC.DN.Co.Model.p = c(bootSig(model$data, bootcopulaprcpndnbi, 4,3)[1:4], NA, bootSig(model$data, bootcopulaprcpndnbi, 4,3)[5:7])
)

# Calculate results with copula for Perceived Response Efficacy, Perceived Response Costs, Perceived Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copulapreprcpndnbi <- lm(BI ~ PRE + PRC + PN + DN + PRE_star + PRC_star + PN_star + DN_star + 0)
summary(copulapreprcpndnbi)
# Bootstrap Standard Errors
bootcopulapreprcpndnbi <- Boot(copulapreprcpndnbi)
summary(bootcopulapreprcpndnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapreprcpndnbi, 4,4)
# Attach to df
bidf <- bidf %>% cbind(
  PRE.PRC.PN.DN.Co.Model.Value = c(summary(bootcopulapreprcpndnbi)[,5]),
  PRE.PRC.PN.DN.Co.Model.p = c(bootSig(model$data, bootcopulapreprcpndnbi, 4,4))
)

datatable(bidf) %>%
  formatRound(-1,
              digits = 3)
```


The copula for Perceived Response Efficacy achieves a significant p-value in some constellations (p < 0.1).
Further, adding the single copula increases the Perceived Response Efficacy coefficient by about 0.05.
Both of this indicates that Perceived Response Efficacy might be endogenous.
There is nothing pointing to hidden endogeneity in any of the other predictors.

The copula will be integrated in the final model to improve the model.

<!-- ```{r model with copula} -->
<!-- modelwc <- estimate_pls(data = model$data %>% cbind(PRE_star),  -->
<!--                         measurement_model = constructs( -->
<!--                         composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--                         composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--                         composite("Benevolence", multi_items("CODI", 1:3)), -->
<!--                         composite("Competence", multi_items("CODI", 4:6)), -->
<!--                         composite("Integrity", multi_items("CODI", 7:9)), -->
<!--                         higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!--                         composite("Knowledge", single_item("COKN")), -->
<!--                         composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--                         composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--                         composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B), -->
<!--                         composite("Copula Perceived Response Efficacy", single_item("PRE_star")) -->
<!--                         ),  -->
<!--   structural_model = relationships( -->
<!--   paths(from = c("Distrusting Beliefs"), to = c("Perceived Response Efficacy", "Perceived Response Costs")), -->
<!--   paths(from = c("Knowledge"), to = c("Perceived Response Efficacy")), -->
<!--   paths(from = c("Perceived Response Efficacy", "Perceived Response Costs", "Personal Moral Norm", "Descriptive Norm", "Copula Perceived Response Efficacy"), to = "Behavioral Intention") -->
<!-- )) -->
<!-- saveRDS(modelwc, "Models/model-co-3-b-2-cop.RDS") -->
<!-- bootmodelwc <- bootstrap_model(modelwc, nboot = 5000) -->
<!-- saveRDS(bootmodelwc, "Models/model-boot-co-3-b-2-cop.RDS") -->
<!-- bootfsmodel <- bootstrap_model(modelwc$first_stage_model, nboot = 5000) -->
<!-- saveRDS(bootmodelwc, "Models/model-fs-boot-co-3-b-2-cop.RDS") -->
<!-- proxymodelwc <- estimate_pls(data = as.data.frame(model$data %>% cbind(PRE_star)),  -->
<!--                         measurement_model = constructs( -->
<!--                         composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--                         composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--                         composite("Distrusting Beliefs", multi_items("CODI", 1:9), weights = mode_B), -->
<!--                         composite("Knowledge", single_item("COKN")), -->
<!--                         composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--                         composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--                         composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B), -->
<!--                         composite("Copula Perceived Response Efficacy", single_item("PRE_star")) -->
<!--                         ),  -->
<!--   structural_model = relationships( -->
<!--   paths(from = c("Distrusting Beliefs"), to = c("Perceived Response Efficacy", "Perceived Response Costs")), -->
<!--   paths(from = c("Knowledge"), to = c("Perceived Response Efficacy")), -->
<!--   paths(from = c("Perceived Response Efficacy", "Perceived Response Costs", "Personal Moral Norm", "Descriptive Norm", "Copula Perceived Response Efficacy"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- saveRDS(proxymodelwc, "Models/model-proxy-co-3-b-2-cop.RDS") -->
<!-- ``` -->

