---
title: "COVID-19 Model Iteration 3-b-2 with copula Structural Model Evaluation"
output: 
  distill::distill_article
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
# Load models and create summaries
# Load PLS Model
model <- readRDS("Models/model-co-3-b-2-cop.RDS")
bootmodel <- readRDS("Models/model-boot-co-3-b-2-cop.RDS")
# Load bootstrapped first stage PLS model
bootfsmodel <- readRDS("Models/model-fs-boot-co-3-b-2-cop.RDS")
# Load approximation PLS model (no HOCs, data formatted as data.frame)
proxymodel <- readRDS("Models/model-proxy-co-3-b-2-cop.RDS")
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Set seminr plot theme
thm <-
  seminr_theme_create(
    construct.compositeA.arrow = "backward",
    construct.compositeA.use_weights = FALSE,
    plot.adj = FALSE,
    construct.compositeA.shape = "ellipse",
    construct.compositeB.shape = "ellipse",
      
  )
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots
## Structural Model Only
This is a path model showing only the structural model components.
```{r plot mm model, echo=FALSE}
plot(bootmodel)
```

# Collinearity
Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.
```{r collinearity vif, echo = FALSE}
vif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(summo$vif_antecedents)){
  x = names(summo$vif_antecedents[i])
  for (j in 1:length(summo$vif_antecedents[[{{x}}]])){
    y = names(summo$vif_antecedents[[{{x}}]])[j]
    vif <- vif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = summo$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                      VIF = double ())
for (i in 1:length(sumfs$vif_antecedents)){
  x = names(sumfs$vif_antecedents[i])
  for (j in 1:length(sumfs$vif_antecedents[[{{x}}]])){
    y = names(sumfs$vif_antecedents[[{{x}}]])[j]
    locvif <- locvif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = sumfs$vif_antecedents[[{{x}}]][j]))
  }
}
locvif <- locvif %>% filter(!(Exogenous.Construct %in% vif$Exogenous.Construct & Endogenous.Construct %in% vif$Endogenous.Construct))
vif <- union(vif, locvif)
datatable(vif,
          filter = 'top',
          options = list(pageLength = nrow(vif)),
          rownames = FALSE,
          colnames = c('Exogenous Construct' = 1,
                        'Endogenous Construct' = 2),
          caption = 'Results of the structural collinearity assessment') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```
VIF is above 3 for some constructs, specifically lower-order constructs.
But it is not above 5 for any constructs.
There is no VIF information for the relationship Distrusting Beliefs - Perceived Response Costs.

# In-sample predictive power
In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.
```{r in-sample pp r^2, echo=FALSE}
r2hoc <- data.frame(Construct = colnames(summo$paths),
                    "R^2" = summo$paths[1,],
                    "AdjR^2" = summo$paths[2,])
r2loc <- data.frame(Construct = colnames(sumfs$paths),
                    "R^2" = sumfs$paths[1,],
                    "AdjR^2" = sumfs$paths[2,]) %>%
  filter(Construct %notin% r2hoc$Construct)
r2 <- union(r2hoc, r2loc)
datatable(r2,
          filter = 'top',
          options = list(pageLength = nrow(r2)),
          rownames = FALSE,
          colnames = c('R²' = 2,
                        'R²adj' = 3),
          caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.249,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```
All R² values are above 0.25, indicating weak in-sample predictive power at a minimum.
For Behavioral Intention, R² is above 0.5, indicating moderate in-sample predictive power.

# Effect size
Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
smhoc <- data.frame(model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target)
hocf2vec <- c()
for (i in 1:nrow(smhoc)){
  x = smhoc[i,1]
  y = smhoc[i, 2]
hocf2vec <- append(hocf2vec, summo$fSquare[[{{x}},{{y}}]])  
}
hocf2 <- smhoc %>% cbind(hocf2vec) %>% rename('f^2' = 3)
smloc <- data.frame(model$first_stage_model$smMatrix) %>% 
  rename('Exogenous Construct' = source,
         'Endogenous Construct' = target) %>%
  filter('Exogenous Construct' %notin% smhoc$`Exogenous Construct`)
locf2vec <- c()
for (i in 1:nrow(smloc)){
  x = smloc[i,1]
  y = smloc[i, 2]
locf2vec <- append(locf2vec, sumfs$fSquare[[{{x}},{{y}}]])  
}
locf2 <- smloc %>% cbind(locf2vec) %>% rename('f^2' = 3) %>% 
  filter(!(`Exogenous Construct` %in% hocf2$`Exogenous Construct` & `Endogenous Construct` %in% hocf2$`Endogenous Construct`))
f2 <- union(hocf2, locf2)
datatable(f2,
          filter = 'top',
          options = list(pageLength = nrow(f2)),
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00')))
```
Benevolence has only an effect on Perceived Response Costs.
Integrity has only an effect on Perceived Response Efficacy.
Other than that, all effects are small at a minimum.
The effect of Perceived Response Efficacy on Behavioral Intention is medium.
The effect of Distrusting Beliefs on Perceived Response Efficacy and Perceived REsponse Costs is large.

# Out-of-sample predictive power
Out of sample predictive power has to be evaluated using a simplified model without HOCs as an approximation as seminr as of now does not support plspredict for HOC
If the root mean square error (RMSE) or the mean absolute deviation (MAD) of the naive LM model is below the ones for the PLS model, this indicates a lack of predictive power.
```{r plspredict, echo = FALSE}
plspre <- predict_pls(proxymodel, noFolds = 50, technique = predict_DA)
sumplspre <- summary(plspre)
oospp <- (as.data.frame(sumplspre$PLS_out_of_sample) %>%
  rbind(as.data.frame(sumplspre$LM_out_of_sample)) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[1,] - (as.data.frame(sumplspre$PLS_out_of_sample))[1,]) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[2,] - (as.data.frame(sumplspre$PLS_out_of_sample))[2,])  %>%
  cbind(`Prediction Errors` = c("PLS RMSE", "PLS MAD", "LM RMSE", "LM MAD", "RMSE Difference", "MAD Difference")))[c(1,3,5,2,4,6),c(ncol(sumplspre$PLS_out_of_sample)+1,1:ncol(sumplspre$PLS_out_of_sample))]
datatable(oospp,
          options = list(pageLength = nrow(oospp)),
          rownames = FALSE,
          caption = 'Out-of-sample predictive power') %>%
  formatRound(-1,
              digits = 3) %>%
  formatStyle(names(oospp), backgroundColor = styleInterval(cuts = c(0), values = c('#ff9999', '#00')))
```
No indicator is predicted better by the model than the LM in terms of both RMSE and MAD.
This points to a lack of out-of-sample predictive power.

# Significance and relevance of path coefficients
Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.
```{r path-coeff, echo = FALSE}
pcbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pcbasesplit <- base::strsplit(pcbase$Construct.Rel., "  ->  ")
pcbasesplit1 <- c()
pcbasesplit2 <- c()
for (i in 1:length(pcbasesplit)){
  pcbasesplit1 <- append(pcbasesplit1, pcbasesplit[[i]][1])
  pcbasesplit2 <- append(pcbasesplit2, pcbasesplit[[i]][2])
}
pclocbase <- rownames_to_column(as.data.frame(sumbofsmo$bootstrapped_paths)) %>% rename (
  Construct.Rel. = rowname)
pclocbasesplit <- base::strsplit(pclocbase$Construct.Rel., "  ->  ")
pclocbasesplit1 <- c()
pclocbasesplit2 <- c()
for (i in 1:length(pclocbasesplit)){
  pclocbasesplit1 <- append(pclocbasesplit1, pclocbasesplit[[i]][1])
  pclocbasesplit2 <- append(pclocbasesplit2, pclocbasesplit[[i]][2])
}
pcdf <- (pcbase %>% 
  mutate('Exogenous Construct' = pcbasesplit1, 
         'Endogenous Construct' = pcbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pcbase$`T Stat.`),
         p = pt(abs(pcbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pcbase$`2.5% CI` < 0 &  pcbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pcdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- (pclocbase %>% 
  mutate('Exogenous Construct' = pclocbasesplit1, 
         'Endogenous Construct' = pclocbasesplit2,
         Construct.Rel. = NULL,
         t = abs(pclocbase$`T Stat.`),
         p = pt(abs(pclocbase$`T Stat.`), nrow(model$data), lower.tail = FALSE),
         '0 in CI' = ifelse(pclocbase$`2.5% CI` < 0 &  pclocbase$`97.5% CI` > 0, TRUE, FALSE),)
  )[,c(7:8,1:3,5:6,11,9:10)]
colnames(pclocdf)[9] <- paste0("t(", nrow(model$data), ")")
pclocdf <- pclocdf %>% filter(!(`Exogenous Construct` %in% pcdf$`Exogenous Construct` & `Endogenous Construct` %in% pcdf$`Endogenous Construct`))
pcalldf <- union(pcdf, pclocdf)
datatable(pcalldf,
          filter = 'top',
          options = list(pageLength = nrow(pcalldf)),
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcalldf)[9], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```

The only insignificant paths are those from Integrity to Perceived Response Costs and from Benevolence to Perceived Response Efficacy.
All other paths are significant.

# Summary table
```{r summary table-df, echo = FALSE, include = FALSE, layout = "l-page"}
sumsm <- pcdf[,-c(5:7)] %>% 
  left_join(hocf2)  %>%
  left_join(vif %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                           'Endogenous Construct' = 'Endogenous.Construct')) %>%
  rename('Path Coefficient Original Estimate' = 'Original Est.',
    'Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
         '0 in Path Coefficient CI' = '0 in CI',
         'Path Coefficient p' = 'p')
colnames(sumsm)[6] <- paste0("Path Coefficient t(", nrow(model$data), ")")
```
```{r summary table-df print, echo = FALSE}
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          caption = 'Structural Model Summary') %>%
  formatRound(c(3:4,6:9),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[6], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('f^2', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00'))) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

# Results summary
All construct and higher-order construct paths are significant and the effect sizes are sufficiently large.
This model can be compared with others.

```{r table-getter, echo = FALSE, include = FALSE}
write_excel_csv(sumsm %>% 
                  mutate(across(c(3:4, 6, 8:9),  round, 2)) %>% 
                  mutate(across(c(7),  round, 3)), 
                "smeval-co-3-b-2-cop.csv", delim = ";")
plot(bootmodel)
save_plot("finalcovmodel.pdf")
```
